---
title: "Report COVID study EN V101"
author: "Thijs de Boer"
date: "2021"
output:
  html_document:
    code_folding: hide
    fig_captions: yes
    highlight: haddock
    number_sections: yes
    theme: flatly
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
      toc_depth: 3
---


Last update: `r Sys.time()`

```{r set-global-options, echo = FALSE}
knitr::opts_chunk$set(eval = TRUE, 
                      echo = TRUE, 
                      message=FALSE,
                      warning = FALSE,
                      cache = FALSE,
                      include = TRUE,
                      collapse = FALSE,
                      dependson = NULL,
                      engine = "R", #  Chunks will always have R code, unless noted
                      error = TRUE,
                      fig.path="Figures/",  #  Set the figure options
                      fig.align = "left",
                      fig.width = 6,
                      fig.height = 4)
```

```{r silent-packages, echo = FALSE, eval = TRUE, message=FALSE, include = FALSE}
library(sjPlot)
library(sjstats)
library(tidyverse)
library(car)
library(ggthemes)
library(kableExtra)
library(ggpubr)
library(scales)
library(ggpmisc)
library(tadaatoolbox)
library(rockchalk)
library(lme4)
```

```{r}
load("C:/Users/Thijs/surfdrive/COVID vaccine/R data/git/EN/.RData")

set_theme(
  base=theme_blank(),
  geom.outline.size = 0.01,
  geom.outline.color = "white", 
  geom.label.size = 3,
  geom.label.color = "grey50")
```

# Population

Total number of participants:
```{r}
df.total %>% nrow()
```

Number of participants that failed the attention test:
```{r}
df.total %>% nrow() - df.total %>% filter(IMC=="1") %>% nrow()
```

Participants between 0-17:
```{r}
df.total %>% filter(age < 18) %>% nrow()
```

Percentage of participants who are at least 18 years old and did not fail the IMC:
```{r}
percent((df.def %>% nrow() / df.total %>% nrow()))
```

Number of participants in this analysis:
```{r}
df.def%>% nrow()
```

Number of participants in the final dataset that failed the manipulation check:
```{r}
df.def %>% nrow() - df.def %>% filter(manipulation.check=="1") %>% nrow()
```

Which is:
```{r}
percent(df.def %>% filter(manipulation.check!="1") %>% nrow() / df.def %>% nrow(), accuracy = 0.01)
```

<br>


# Experiment: Perceived independence of EMA

<br>

## Randomisation check
This table shows how many respondents are assigned to each experimental group.
```{r}
df.def %>%
  group_by(experimental.group) %>%
  tally()
```

<br>

## Description
```{r}
df.def %>% 
sjmisc::descr(perceived.independence.reversed, show = c("n", "NA.prc", "mean", "sd", "md", "iqr", "trimmed", "range", "skew")) %>%
  kbl(digits= 2) %>%
 kable_paper()
```

<br>

## Histogram
```{r}
df.def %>%
  ggplot(aes(x = perceived.independence.reversed, fill = experimental.group)) +
  geom_bar(width = 0.75,alpha = 0.8, position = position_dodge()) +
  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Independence condition") +  scale_fill_viridis_d(name = "Independence condition") + 
  theme_tufte()
```

<br>

## T-test

<br>

### With complete dataset
```{r}
tadaa_t.test(data = df.def, response = perceived.independence.reversed, group = experimental.group, print = "markdown")
```

<br>

### With those who failed the manipulation check filtered out 
```{r}
tadaa_t.test(data = df.check, response = perceived.independence.reversed, group = experimental.group, print = "markdown")
```

<br>

# Time

<br>

```{r include=FALSE}
table.duration <- df.def %>%
  dplyr::summarize(mean = mean(duration),
            sd = sd(duration),
            min = min(duration),
            q1 = quantile(duration, probs = 0.25),
            median = median(duration),
            q3 = quantile(duration, probs = 0.75),
            max = max(duration)) %>% round(digits = 2)

table.intro.submit <- df.def %>% 
   dplyr::summarize(mean = mean(intro.submit),
            sd = sd(intro.submit),
            min = min(intro.submit),
            q1 = quantile(intro.submit, probs = 0.25),
            median = median(intro.submit),
            q3 = quantile(intro.submit, probs = 0.75),
            max = max(intro.submit)) %>% round(digits = 2)

table.manipulation.submit <- df.def %>%  
   dplyr::summarize(mean = mean(manipulation.submit),
            sd = sd(manipulation.submit),
            min = min(manipulation.submit),
            q1 = quantile(manipulation.submit, probs = 0.25),
            median = median(manipulation.submit),
            q3 = quantile(manipulation.submit, probs = 0.75),
            max = max(manipulation.submit)) %>% round(digits = 2)

table.decision.submit <- df.def %>% 
   dplyr::summarize(mean = mean(decision.submit),
            sd = sd(decision.submit),
            min = min(decision.submit),
            q1 = quantile(decision.submit, probs = 0.25),
            median = median(decision.submit),
            q3 = quantile(decision.submit, probs = 0.75),
            max = max(decision.submit)) %>% round(digits = 2)
```

<br>

## Survey duration

<br>

### Histogram
```{r}
df.def %>% filter(duration < 30) %>% 
plot_frq((duration),
        geom.colors = alpha("red",0.8),
        type = "hist",
        geom.size = 0.25) +
  theme(axis.text = element_text(face = "bold",  size= 9)) + labs(title = "Total survey duration") +  scale_x_continuous(name="Time in minutes", breaks = seq(0,30, 2)) +  scale_y_continuous(expand = expansion(c(0, 0.25))) + annotate(geom = "table", x = Inf, y = Inf, label = list(table.duration))
```

<br>

### Relationship between perceived independence and total survey duration
```{r}
df.def %>% filter(duration < 30) %>% ggplot(aes(duration, perceived.independence.reversed, fill = experimental.group)) + geom_jitter() + geom_smooth() + scale_x_continuous("Survey duration (minutes)", limits = c(0,30)) + scale_y_continuous("Perceived indepdence", breaks = 1:7) + scale_fill_viridis_d(name = "Independence condition") + theme_light()
```

<br>

## Do participants read the information about the case?

<br>

### Page submission - introduction of case
```{r}
df.def %>% filter(intro.submit < 100) %>%  
plot_frq((intro.submit),
        geom.colors = alpha("dodgerblue2",0.8),
        type = "hist",
        geom.size = 1) + 
  theme(axis.text = element_text(face = "bold",  size= 9)) +
  scale_x_continuous(name="Time in seconds",breaks = seq(0,100,5)) +   scale_y_continuous(expand = expansion(c(0, 0.1))) + annotate(geom = "table", x = Inf, y = Inf, label = list(table.intro.submit))
```

<br>

### Page submission - manipulation

<br>

*Histogram*
```{r}
df.def %>% filter(manipulation.submit < 100) %>%
plot_frq((manipulation.submit),
        geom.colors = alpha("dodgerblue2",0.8),
        type = "hist",
        geom.size = 1) +
  theme(axis.text = element_text(face = "bold",  size= 9)) +
  scale_x_continuous(name="Time in seconds",breaks = seq(0,100,5)) +   scale_y_continuous(expand = expansion(c(0, 0.1))) + annotate(geom = "table", x = Inf, y = Inf, label = list(table.manipulation.submit))
```

<br>

*Relationship between perceived independence and time spent on the page with the manipulation*
```{r}
df.def %>% filter(manipulation.submit < 60) %>% ggplot(aes(manipulation.submit, perceived.independence.reversed, fill = experimental.group)) + geom_jitter() + geom_smooth() + scale_x_continuous("Page submission - manipulation (seconds)", limits = c(0,60)) + scale_y_continuous("Perceived indepdence", breaks = 1:7) + scale_fill_viridis_d(name = "Independence condition") + theme_light()
```

<br>

*Broken down in quartiles (+ group size and SE)*
```{r}
give.n <- function(x){
  return(c(y = mean(x)*1.1, label = length(x))) 
}

ggline(df.def, x = "manipulation.submit.quartile", y = "perceived.independence.reversed", color = "experimental.group", ylab = "Perceived independence", xlab = "Page submission - manipulation (quartiles)",  add = "mean_se", ylim = c(2, 4.5), yticks.by = 0.5) +
  stat_summary(fun.data = give.n, geom = "text", fun = median, size = 4, col = "black")
```

<br>

*Split dataset with 30 seconds as cut-off point (+ group size and SE)*
```{r}
ggline(df.def, x = "manipulation.submit.30", y = "perceived.independence.reversed", color = "experimental.group", ylab = "Perceived independence", xlab = "",  add = c("mean_se"), ylim = c(2, 4), yticks.by = 0.5) +
  stat_summary(fun.data = give.n, geom = "text", fun = median, size = 4, col = "black")
```

### Page submission - EMA's decision
```{r}
df.def %>% filter(decision.submit < 100) %>% 
plot_frq((decision.submit),
        geom.colors = alpha("dodgerblue2",0.8),
        type = "hist",
        geom.size = 1) + 
  theme(axis.text = element_text(face = "bold",  size= 9)) +
  scale_x_continuous(name= "Time in seconds", breaks = seq(0,100,5)) +   scale_y_continuous(expand = expansion(c(0, 0.1))) + annotate(geom = "table", x = Inf, y = Inf, label = list(table.decision.submit))
```

<br>

### Time and ...

<br>

***...Failing the manipulation check***

```{r}
p1 <- df.def %>% filter(duration < 30) %>% ggplot(aes(x= duration, color = manipulation.check.failed, fill = manipulation.check.failed)) + geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 2) +
 geom_density(alpha= .1, linetype= "dashed") + labs(title = "Total survey duration", x = "minutes") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

p2  <- df.def %>% filter(intro.submit < 60) %>% ggplot(aes(x= intro.submit, color = manipulation.check.failed, fill = manipulation.check.failed)) + geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 5) +
 geom_density(alpha= .1, linetype= "dashed") + labs(title = "Page submission - introduction", x = "seconds") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

p3 <- df.def %>% filter(manipulation.submit < 60) %>% ggplot(aes(x=manipulation.submit, color = manipulation.check.failed, fill = manipulation.check.failed)) + geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 5) + geom_density(alpha= .1, linetype= "dashed") + labs(title = "Page submission - manipulation", x = "seconds") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

p4 <- df.def %>% filter(decision.submit < 60) %>% ggplot(aes(x=decision.submit, color =manipulation.check.failed, fill = manipulation.check.failed)) + 
 geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 5) +
 geom_density(alpha= .1, linetype= "dashed") + labs(title = "Page submission - EMA's decision", x = "seconds", color = "Manipulation Check") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

ggarrange(p1, p2, p3, p4, nrow = 2, ncol = 2, labels="AUTO", legend = "bottom", common.legend = TRUE)
```

<br>

***...experimental groups***

```{r}
p5 <- df.def %>% filter(duration < 30) %>% ggplot(aes(x= duration, color = experimental.group, fill = experimental.group)) + geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 2) +
 geom_density(alpha= .1, linetype= "dashed") + labs(title = "Total survey duration", x = "minutes") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

p6  <- df.def %>% filter(intro.submit < 60) %>% ggplot(aes(x= intro.submit, color = experimental.group, fill = experimental.group)) + geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 5) +
 geom_density(alpha= .1, linetype= "dashed") + labs(title = "Page submission - introduction", x = "seconds") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

p7 <- df.def %>% filter(manipulation.submit < 60) %>% ggplot(aes(x=manipulation.submit, color = experimental.group, fill = experimental.group)) + geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 5) + geom_density(alpha= .1, linetype= "dashed") + labs(title = "Page submission - manipulation", x = "seconds") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

p8 <- df.def %>% filter(decision.submit < 60) %>% ggplot(aes(x=decision.submit, color = experimental.group, fill = experimental.group)) +
 geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 5) +
 geom_density(alpha= .1, linetype= "dashed") + labs(title = "Page submission - EMA's decision", x = "seconds", color = "Manipulation Check") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

ggarrange(p5, p6, p7, p8, nrow = 2, ncol = 2, labels="AUTO", legend = "bottom", common.legend = TRUE)
```

<br>

T-tests (outliers removed - i.e., cases outside 1.5 times the interquartile range):
```{r include=FALSE}
out.duration <- boxplot(df.def$duration, plot=FALSE)$out
out.duration <-df.def[-which(df.def$duration %in% out.duration),]

out.intro.submit <- boxplot(df.def$intro.submit, plot=FALSE)$out
out.intro.submit <-df.def[-which(df.def$intro.submit %in% out.intro.submit),]

out.manipulation.submit <- boxplot(df.def$manipulation.submit, plot=FALSE)$out
out.manipulation.submit <-df.def[-which(df.def$manipulation.submit %in% out.manipulation.submit),]

out.decision.submit <- boxplot(df.def$decision.submit, plot=FALSE)$out
out.decision.submit <-df.def[-which(df.def$decision.submit %in% out.decision.submit),]
```

***Survey duration***
```{r}
tadaa_t.test(data = out.duration, response = duration, group = experimental.group, print = "markdown")
```

***Page submission - Introduction***
```{r}
tadaa_t.test(data = out.intro.submit, response = intro.submit, group = experimental.group, print = "markdown")
```

***Page submission - manipulation***
```{r}
tadaa_t.test(data = out.manipulation.submit, response = manipulation.submit, group = experimental.group, print = "markdown")
```

***Page submission - decision***
```{r}
tadaa_t.test(data = out.decision.submit, response = decision.submit, group = experimental.group, print = "markdown")
```

<br>

***...interface (pc/mobile)***

```{r}
p9 <- df.def %>% filter(duration < 30) %>% ggplot(aes(x= duration, color = device, fill = device)) + geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 2) +
 geom_density(alpha= .1, linetype= "dashed") + labs(title = "Total survey duration", x = "minutes") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

p10 <- df.def %>% filter(intro.submit < 60) %>% ggplot(aes(x= intro.submit, color = device, fill = device)) + geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 5) +
 geom_density(alpha= .1, linetype= "dashed") + labs(title = "Page submission - introduction", x = "seconds") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

p11 <- df.def %>% filter(manipulation.submit < 60) %>% ggplot(aes(x=manipulation.submit, color = device, fill = device)) + geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 5) + geom_density(alpha= .1, linetype= "dashed") + labs(title = "Page submission - manipulation", x = "seconds") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

p12 <- df.def %>% filter(decision.submit < 60) %>% ggplot(aes(x=decision.submit, color = device, fill = device)) +
 geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 5) +
 geom_density(alpha= .1, linetype= "dashed") + labs(title = "Page submission - EMA's decision", x = "seconds", color = "Manipulation Check") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

ggarrange(p9, p10, p11, p12, nrow = 2, ncol = 2, labels="AUTO", legend = "bottom", common.legend = TRUE)
```

<br>

# Vaccination intention
```{r}
df.def %>%
plot_frq(intent.vaccine,
        title = "Vaccination intention") + 
  theme_blank() +
  theme(axis.title  = element_blank())
```

<br>

## Open question
```{r}
df.def %>% 
  filter(nchar(Q16.3)>1) %>% 
  select(Q16.3) %>% 
  kable() %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%    scroll_box(height = "400px")
```

<br>

# Interface (mobile/pc)

<br>

## Distribution
```{r}
df.def %>%
  plot_frq(device,
        ylim = c(0,nrow(df.def)),
        geom.colors = alpha("dodgerblue1",0.8))+
  theme_blank()
```

<br>

## Distribution of perceived independence for mobile/pc
```{r}
p13 <- df.def %>%
  drop_na(perceived.independence.reversed) %>% filter(device == "pc") %>% 
  ggplot(aes(x = perceived.independence.reversed, fill = experimental.group)) + labs(title = "PC") + 
  geom_bar(width = 0.8, alpha = 1, position = position_dodge()) +
  scale_x_continuous(name="Perceived independence", breaks = 1:7) + scale_y_continuous(name="") + scale_fill_manual(name = "Independence condition", values = c("dodgerblue2","dodgerblue4")) +
theme(plot.title = element_text(face = "bold")) +  scale_fill_viridis_d(name = "Independence condition")

p14 <- df.def %>% filter(device == "mobile") %>% 
  ggplot(aes(x = perceived.independence.reversed, fill = experimental.group)) + labs(title = "Mobile") + 
  geom_bar(width = 0.8, alpha = 1, position = position_dodge())+
  scale_x_continuous(name="Perceived independence", breaks = 1:7) + scale_y_continuous(name="") + scale_fill_manual(name = "Independence condition", values = c("dodgerblue2","dodgerblue4")) +
theme(plot.title = element_text(face = "bold")) +  scale_fill_viridis_d(name = "Independence condition")

ggarrange(p13, p14,
          ncol = 2,nrow = 1, common.legend = TRUE, labels = "AUTO")
```

<br>

### T-test
```{r}
tadaa_t.test(data = df.def, response = perceived.independence.reversed, group = device, print = "markdown")
```

<br>

# Descriptive statistics

<br>

## Demography

**Age**
```{r}
age.population.5 <- read.csv("AGE_POPULATION_SEGMENTS_EN_25012021.csv")
age.total <- merge(age.population.5, age.sample, by.x = "ï..age", by.y = ".")

age.total <- age.total %>% 
  rename(age.category = ï..age,
  count.population = count,
  count.sample = n,
  percentage.population = percentage.x,
  percentage.sample = percentage.y)

age.total$age.category <- factor(age.total$age.category, levels = c(
"younger than 25",
"25-29",           "30-34",           "35-39",          
"40-44",           "45-49",           "50-54",          
"55-59",           "60-64",           "65-69",          
"70-74",           "75-79",           "80 or older"))    

age.total %>% select(age.category, percentage.population, percentage.sample) %>% reshape2::melt(id.vars = 'age.category', variable.name = 'series')  %>% ggplot(aes(age.category, value, colour = series, fill = series)) + geom_bar (stat="identity", width=0.9, position = position_dodge(width=0.9)) + 
  theme_blank() + theme(legend.position="top", axis.text.x = element_text(angle = 45, hjust = 1), axis.title  = element_blank()) + scale_y_continuous(labels=scales::percent)
```

<br>

**Gender**
```{r}
df.def %>% 
plot_frq(female,
                ylim = c(0,nrow(df.def)),
        axis.labels = c("Male","Female"),
        title = "Gender")+ 
  theme_blank()
```

<br>

**Education**
```{r}
education.population <- read.csv("EDUCATION_EN-25012021.csv")

education.sample <-  df.def %>% drop_na(education.recoded)  %>%  count(education.recoded) %>% 
  mutate(percentage = n / sum(n))

education.total <- merge(education.population, education.sample, by.x = "level", by.y = "education.recoded", all = TRUE)

education.total <- education.total %>% 
  rename(education.category = level,
  count.population = count,
  count.sample = n,
  percentage.population = percentage.x,
  percentage.sample = percentage.y)

education.total %>% select(education.category, percentage.population, percentage.sample) %>% reshape2::melt(id.vars = 'education.category', variable.name = 'series')  %>% ggplot(aes(education.category, value, colour = series, fill = series)) + geom_bar (stat="identity", width=0.9, position = position_dodge(width=0.9)) + 
  theme_blank() + theme(legend.position="bottom", axis.title  = element_blank()) + coord_flip() + scale_y_continuous(labels=scales::percent)
```

<br>

**Income**
```{r}
df.def %>% 
  filter(income!=0) %>% 
  plot_frq(income,
        ylim = c(0,nrow(df.def)/2.5),
        title = "Participant income level") + 
  theme_blank() + theme(axis.text.x = element_text(angle = 45, hjust = 1), axis.title  = element_blank())
```

<br>

**Province**
```{r echo=FALSE}
provinces.population <- read.csv("PROVINCE_EN-25012021.csv")
provinces.sample <-  df.def %>% drop_na(province)  %>%  count(province) %>% 
  mutate(percentage = n / sum(n))

provinces.total <- merge(provinces.sample, provinces.population, by = "province")

provinces.total <- provinces.total %>% 
  rename(count.population = count,
  count.sample = n,
  percentage.sample = percentage.x,
  percentage.population = percentage.y)

provinces.total %>% select(province, percentage.population, percentage.sample) %>% reshape2::melt(id.vars = 'province', variable.name = 'series')  %>% ggplot(aes(province, value, colour = series, fill = series)) + geom_bar (stat = "identity", width = 0.5, position = position_dodge(width = 0.9)) + 
  theme_blank() + theme(legend.position="bottom", axis.title  = element_blank(), axis.text.y = element_text(size = 6), aspect.ratio = 1.25/1) + coord_flip() + scale_y_continuous(labels=scales::percent)
```

<br>

**Works in healthcare sector**
```{r}
df.def %>% 
  plot_frq(healthcare,
        ylim = c(0,nrow(df.def)),
        title = "") + 
  theme_blank()
```

<br>

# Pre-post


## Correlation matrix
```{r}
df.def %>% 
  select(credibility.EMA,
         credibility.post,
         credibility.expert,
         credibility.noninterference,
         credibility.stability,
         credibility.index,
         perceived.independence.reversed,
         intent.vaccine,
         ) %>% 
  tab_corr(triangle="lower",
           remove.spaces=T,
           p.numeric = T,
           fade.ns = T,
           digits = 2,
           na.deletion="pairwise",
           title = "Correlation matrix")
```

<br >

## Plot
```{r}
df.def  %>% 
  dplyr::select(experimental.group,
         credibility.EMA,
         credibility.post) %>%  drop_na() %>% 
  gather("key","value",-experimental.group) %>% 
  mutate(key = car::recode(key,"'credibility.EMA'='0.Pre';'credibility.post'='1.Post'")) %>%

ggplot(aes(x=key,y=value,color=experimental.group))+
      stat_summary(fun.data = mean_cl_normal, geom = "errorbar", alpha=0.5,width=0.1,size=1,position=position_dodge(0.5)) + 
  stat_summary(fun = mean, geom = "point", alpha=0.5,size=2,position=position_dodge(0.5))+
  stat_summary(fun = mean, geom = "line", alpha=0.5,size=1,position=position_dodge(0.5), aes(group = experimental.group))+
  theme_tufte()
```

<br >

## Regression
```{r}
t1 <- df.def %>% mutate(id = row_number()) %>% 
  select(experimental.group,
         id,
         credibility.EMA,
         credibility.post) %>%
  drop_na() %>%
  gather("key","value",-experimental.group,-id) %>% 
  mutate(post = key %>% Recode("'credibility.EMA'= 0;'credibility.post'=1"),
         EMA.credibility = value) 


tmod1 <- lmer(EMA.credibility ~ post + +(1|id),
                       data = t1)

tmod2 <- tmod1 %>% update(.~.+experimental.group) 


tmod3 <- tmod2 %>% update(.~. + post*experimental.group)

tab_model(tmod2,tmod3,
          show.ci = F,
          show.se = T,
          collapse.se = T,
          emph.p = F)
```

## Key variables

<br>

### Statistics
```{r}
df.def %>% select(benefits.vaccines, intent.vaccine:importance.NRA, knowledge) %>%
sjmisc::descr(show = c("n", "NA.prc", "mean", "sd", "md", "iqr", "trimmed", "range", "skew")) %>%
  kbl(digits= 2) %>%
 kable_paper()
```

<br>


### Plots
```{r}
df.def %>% select(benefits.vaccines, intent.vaccine:importance.NRA) %>%
  gather() %>% 
  ggplot(aes(value)) +
    facet_wrap(~ key, scales = "free") +
    geom_histogram(boundary = 0.1, binwidth = 0.5) + 
  theme(text = element_text(face = "bold",  size = 6), axis.text.y = element_text(size = 5))
```


# Correlation matrix
```{r}
df.def %>% 
  select(trust.EC:trust.politicians, trust.health.authorities, benefits.vaccines, credibility.index, credibility.EMA, familiarity.EMA, familiarity.advice, consequences.economic, consequences.health, age, perceived.independence.reversed, political.ideology, EU.integration, knowledge, interpersonal.trust, treatment, private.providers) %>% 
  tab_corr(triangle="lower",
           remove.spaces=T,
           p.numeric = T,
           fade.ns = T,
           digits = 2,
           na.deletion="pairwise",
           title = "Correlation matrix")
```

<br>

# Regression

<br>

## Perceived independence
```{r}
reg.perceived.independence1 <- lm(perceived.independence.reversed ~  trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA + familiarity.EMA + familiarity.advice +  political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + poly(age, 2) + healthcare + income,
                    data = df.def,
                    na.action = na.omit)

reg.perceived.independence2 <- lm(perceived.independence.reversed ~ credibility.index + trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA + familiarity.EMA + familiarity.advice +  political.ideology + consequences.health + consequences.economic +  EU.integration + private.providers + knowledge +  experimental.group + female + poly(age, 2) + healthcare + income,
                    data = df.def,
                    na.action = na.omit)


tab_model(reg.perceived.independence1, reg.perceived.independence2,  show.ci = FALSE)
```

<br >

## Vaccination intension
```{r}
reg.intent.vaccine1 <- glm(intent.vaccine.recoded ~ trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA + familiarity.EMA + familiarity.advice +  political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + age + healthcare + income,
                    data = df.def,
                    na.action = na.omit,
                    family = binomial(link = 'logit'))

reg.intent.vaccine2 <- glm(intent.vaccine.recoded ~ credibility.index + trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA + familiarity.EMA + familiarity.advice +  political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + age + healthcare + income,
                    data = df.def,
                    na.action = na.omit,
                    family = binomial(link = 'logit'))

reg.intent.vaccine3 <- glm(intent.vaccine.recoded ~ perceived.independence.reversed + trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA + familiarity.EMA + familiarity.advice +  political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + age + healthcare + income,
                    data = df.def,
                    na.action = na.omit,
                    family = binomial(link = 'logit'))

reg.intent.vaccine4 <- glm(intent.vaccine.recoded ~ credibility.index + perceived.independence.reversed + trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA + familiarity.EMA + familiarity.advice +  political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + age + healthcare + income,
                    data = df.def,
                    na.action = na.omit,
                    family = binomial(link = 'logit'))

tab_model(reg.intent.vaccine1, reg.intent.vaccine2, reg.intent.vaccine3, reg.intent.vaccine4, show.ci = FALSE)
```

<br>

## Crebility of EMA's decision
```{r}
reg.credibility1 <- lm(credibility.index  ~ trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA + familiarity.EMA + familiarity.advice + political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + poly(age, 2) + healthcare + income,
                    data = df.def,
                    na.action = na.omit)

reg.credibility2 <- lm(credibility.index  ~ perceived.independence.reversed + trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA + familiarity.EMA + familiarity.advice +  political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + poly(age, 2) + healthcare + income,
                    data = df.def,
                    na.action = na.omit)

reg.credibility3 <- lm(credibility.index  ~ perceived.independence.reversed + trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA + familiarity.EMA +  + familiarity.advice +  political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + poly(age, 2) + healthcare + income + perceived.independence.reversed:benefits.vaccines + benefits.vaccines:experimental.group,
                    data = df.def,
                    na.action = na.omit)

reg.credibility4 <- lm(credibility.index  ~ perceived.independence.reversed + trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA + familiarity.EMA +  + familiarity.advice +  political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + age.recoded + healthcare + income + perceived.independence.reversed:benefits.vaccines + benefits.vaccines:experimental.group,
                    data = df.def,
                    na.action = na.omit)


reg.credibility3.centered <- meanCenter(reg.credibility3, centerOnlyInteractors = TRUE, centerDV = FALSE)

reg.credibility4.centered <- meanCenter(reg.credibility4, centerOnlyInteractors = TRUE, centerDV = FALSE)

tab_model(reg.credibility1, reg.credibility2, reg.credibility3.centered, show.ci = FALSE)
```


_Note: Interaction variables are centered in the third model_

<br>


### Plots

***Interaction effect: perceived independence x benefits of vaccines***
```{r}
plot_model(reg.credibility3.centered, type = "int", mdrt.values = "meansd")[[1]]
```

***Interaction effect: perceived independence x experimental group***
```{r}
plot_model(reg.credibility3.centered, type = "int", mdrt.values = "meansd")[[2]]
```

***marginal effects: Effect of perceived independence on credibility for different age groups***
```{r}
plot_model(reg.credibility4.centered, type = "pred", terms = c("perceived.independence.reversedc", "age.recoded"))
```

## Full models - filtered

### Perceived independence
```{r}
reg.perceived.independence.30 <- lm(perceived.independence.reversed ~ credibility.index + trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA + familiarity.EMA + familiarity.advice +  political.ideology + consequences.health + consequences.economic +  EU.integration + private.providers + knowledge +  experimental.group + female + poly(age, 2) + healthcare + income,
                    data = df.30,
                    na.action = na.omit)

reg.perceived.independence.check <- lm(perceived.independence.reversed ~ credibility.index + trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA + familiarity.EMA + familiarity.advice +  political.ideology + consequences.health + consequences.economic +  EU.integration + private.providers + knowledge +  experimental.group + female + poly(age, 2) + healthcare + income,
                    data = df.check,
                    na.action = na.omit)

tab_model(reg.perceived.independence.30, reg.perceived.independence.check, dv.labels = c("Perceived independence (filter = page submission)", "Perceived independence (filter = manipulation check)"), show.ci = FALSE)
```

### Vaccination intention
```{r eval=FALSE, include=FALSE}
reg.intent.vaccine.30 <- glm(intent.vaccine.recoded ~ credibility.index + perceived.independence.reversed + trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA + familiarity.EMA + familiarity.advice +  political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + age + healthcare + income,
                    data = df.30,
                    na.action = na.omit,
                    family = binomial(link = 'logit'))

reg.intent.vaccine.check  <- glm(intent.vaccine.recoded ~ credibility.index + perceived.independence.reversed + trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA + familiarity.EMA + familiarity.advice +  political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + age + healthcare + income,
                    data = df.check,
                    na.action = na.omit,
                    family = binomial(link = 'logit'))

tab_model(reg.intent.vaccine.30, reg.intent.vaccine.check, dv.labels = c("Vaccination intention (filter = page submission)", "Vaccination intention (filter = manipulation check)"), show.ci = FALSE)
```

Too few cases.

### Credibility index
```{r}
reg.credibility.30 <- lm(credibility.index  ~ perceived.independence.reversed + trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA + familiarity.EMA +  + familiarity.advice +  political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + poly(age, 2) + healthcare + income + perceived.independence.reversed:benefits.vaccines + benefits.vaccines:experimental.group,
                    data = df.30,
                    na.action = na.omit)

reg.credibility.check <- lm(credibility.index  ~ perceived.independence.reversed + trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA + familiarity.EMA +  + familiarity.advice +  political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + poly(age, 2) + healthcare + income + perceived.independence.reversed:benefits.vaccines + benefits.vaccines:experimental.group,
                    data = df.check,
                    na.action = na.omit)

tab_model(reg.credibility.30, reg.credibility.check, dv.labels = c("Credibility (filter = page submission)",  "Credibility (filter = manipulation check)"), show.ci = FALSE)
```

<br>

# Familiarity
```{r}
p15 <-  df.def %>% ggplot(aes(familiarity.advice, perceived.independence.reversed)) + geom_jitter() + geom_smooth(method = "lm") + scale_x_continuous("Familiarity advice", breaks = 1:7) + scale_y_continuous("Perceived independence", breaks = 1:7) + labs(title = "Advice") + theme_light()

p16 <-  df.def %>% ggplot(aes(familiarity.EMA, perceived.independence.reversed)) + geom_jitter() + geom_smooth(method = "lm") + scale_x_continuous("Familiarity EMA", breaks = 1:7) + scale_y_continuous("Perceived independence", breaks = 1:7) + labs(title = "EMA") + theme_light()

ggarrange(p15, p16,
          ncol = 2,nrow = 1)
```

<br>

# Remarks from participants
```{r}
df.total %>% 
  filter(nchar(comments.general)>1) %>% 
  select(comments.general) %>% 
  kable() %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%    scroll_box(height = "400px")
```