---
title: "Report COVID study POOLED V100"
author: "Thijs de Boer"
date: "2021"
output:
  html_document:
    code_folding: hide
    fig_captions: yes
    highlight: haddock
    number_sections: yes
    theme: flatly
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
      toc_depth: 3
---


Last update: `r Sys.time()`

```{r set-global-options, echo = FALSE}
knitr::opts_chunk$set(eval = TRUE, 
                      echo = TRUE, 
                      message=FALSE,
                      warning = FALSE,
                      cache = FALSE,
                      include = TRUE,
                      collapse = FALSE,
                      dependson = NULL,
                      engine = "R", #  Chunks will always have R code, unless noted
                      error = TRUE,
                      fig.path="Figures/",  #  Set the figure options
                      fig.align = "left",
                      fig.width = 6,
                      fig.height = 4)
```

```{r silent-packages, echo = FALSE, eval = TRUE, message=FALSE, include = FALSE}
library(sjPlot)
library(sjstats)
library(tidyverse)
library(car)
library(ggthemes)
library(kableExtra)
library(ggpubr)
library(scales)
library(ggpmisc)
library(tadaatoolbox)
library(rockchalk)
library(lme4)
library(janitor)
library(sjmisc)
library(lavaan)
library(semPlot)
library(stargazer)
library(semTools)
```

```{r}
load("C:/Users/Thijs/surfdrive/COVID vaccine/git/POOLED/.RData")

set_theme(
  base=theme_blank(),
  geom.outline.size = 0.01,
  geom.outline.color = "white", 
  geom.label.size = 3,
  geom.label.color = "grey50")
```


# Population

Total number of cases, removed cases and final cases (complete cases):
```{r}
t1 <- df.total %>% filter(Finished == 1) %>%  
  group_by(country) %>% 
  tally() %>% 
  mutate(percentage = ((n/nrow(df.total %>% filter(Finished == 1))*100) %>% round(1))) %>%
  adorn_totals("row")

t2 <- df.total %>% filter(Finished == 1 & IMC != 1 | age < 18) %>%  
  group_by(country) %>% 
  tally() %>% 
  mutate(percentage = ((n/nrow(df.total %>% filter(Finished == 1 & IMC != 1 | age < 18))*100) %>% round(1))) %>%
  adorn_totals("row")

t3 <- merge(x = t1, y = t2, by = "country", all.x = TRUE) %>%  mutate(n.final = (n.x-n.y),
        percentage.final = (n.final/nrow(df.total %>% filter(Finished == 1 & IMC == 1 & age >= 18))*100) %>% round(1),
        ratio = ((n.x-n.y)/n.x) %>% round(2)) 

t3 %>% 
  kable(col.names = c("",
                      "n",
                      "%",
                      "n",
                      "%",
                      "n",
                      "%",
                      "Ratio (final/total)"
                      ),
        align=rep('c', 5)) %>% 
    kable_styling(bootstrap_options = c( "condensed",  "striped", "hover"),
                full_width = F,
                position = "left")  %>% add_header_above(c(" ", "Total"  = 2, "Failed IMC or under 18" = 2, "Final" = 2, " "))  %>%
   column_spec(column = 2:8, width = "2cm")
```

One case discrepancy??
```{r}
pooled %>% filter(Finished == 1) %>% nrow
```


Number of participants in the final dataset that failed the comprehension check:
```{r}
t4 <- pooled %>%  filter(Finished == 1) %>%
   group_by(country, comprehension.check.failed)%>%
  summarise(n=n()) %>%
  spread(comprehension.check.failed, n) %>%
  adorn_totals("row")  %>% mutate(
   missing =  `<NA>`,
   missing = tidyr::replace_na(missing, 0),
   total = (failed + passed + missing),
  percentage = (passed/(total)*100) %>% round(2)) %>% relocate(failed, .after = passed)

t4 %>% select(-`<NA>`) %>% 
  kable(col.names = c("",
                      "Passed",
                      "Failed",
                      "Missing",
                      "Total",
                      "% Passed")) %>% 
    kable_styling(bootstrap_options = c("condensed", "striped", "hover"),
                full_width = F,
                position = "left")
```

<br>

# Outcome variables

In this section we provide additional details about out outcome variables -- the three aspects of policy credibility. We report the distributions and correlations of the six survey items. Thereafter, we include the R code and results of our confirmatory factor analysis.   


## Distributions of items

Item 1: I believe that the EMA's opinion was based strictly on scientific considerations. 

```{r}
pooled %>%
  ggplot(aes(x=credibility.item1, fill = experimental.group)) +
  geom_bar(width = 0.75, alpha=0.8)+
  scale_x_continuous(name="",limits = c(0,8),breaks = 1:7)+
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue2","dodgerblue3", "dodgerblue4"))+
  facet_grid(experimental.group ~ country,  margins=TRUE, scale="free") + 
  theme_tufte() +
  theme(legend.position = "none", axis.title = element_blank())
```

<br>

Item 2: I believe that the EMA's opinion was influenced by political interests. (reversed)


```{r}
pooled %>%
  ggplot(aes(x=credibility.item2.reversed, fill = experimental.group)) +
  geom_bar(width = 0.75,alpha=0.8)+
  scale_x_continuous(name="",limits = c(0,8),breaks = 1:7)+
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue2","dodgerblue3", "dodgerblue4"))+
  facet_grid(experimental.group ~ country,  margins=TRUE, scale="free") + 
  theme_tufte() +
  theme(legend.position = "none", axis.title = element_blank())
```


Item 3: I believe that the EMA's opinion was affected by the industry interests. (reversed)


```{r}
pooled %>%
  ggplot(aes(x=credibility.item3.reversed, fill = experimental.group)) +
  geom_bar(width = 0.75,alpha=0.8)+
  scale_x_continuous(name="",limits = c(0,8),breaks = 1:7)+
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue2","dodgerblue3", "dodgerblue4"))+
  facet_grid(experimental.group ~ country,  margins=TRUE, scale="free") + 
  theme_tufte() +
  theme(legend.position = "none", axis.title = element_blank())
```

<br>

Item 4: I believe that the EMA's opinion was formed after evaluating all the relevant data and evidence. 

```{r}
pooled %>%
  ggplot(aes(x=credibility.item4, fill = experimental.group)) +
  geom_bar(width = 0.75,alpha=0.8)+
  scale_x_continuous(name="",limits = c(0,8),breaks = 1:7)+
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue2","dodgerblue3", "dodgerblue4"))+
  facet_grid(experimental.group ~ country,  margins=TRUE, scale="free") + 
  theme_tufte() +
  theme(legend.position = "none", axis.title = element_blank())
```

<br>

Item 5: I believe that the assessment of the evidence was based on adequate methods. 

```{r}
pooled %>%
  ggplot(aes(x=credibility.item5, fill = experimental.group)) +
  geom_bar(width = 0.75,alpha=0.8)+
  scale_x_continuous(name="",limits = c(0,8),breaks = 1:7)+
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue2","dodgerblue3", "dodgerblue4"))+
  facet_grid(experimental.group ~ country,  margins=TRUE, scale="free") + 
  theme_tufte() +
  theme(legend.position = "none", axis.title = element_blank())
```

<br>

Item 6: Assuming that the scientific evidence does not change, I believe that EMA's opinion about the Pfizer-BioNTech vaccine will not change the next time EMA is asked to re-examine it.

```{r}
pooled %>%
  ggplot(aes(x=credibility.item6, fill = experimental.group)) +
  geom_bar(width = 0.75,alpha=0.8)+
  scale_x_continuous(name="",limits = c(0,8),breaks = 1:7)+
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue2","dodgerblue3", "dodgerblue4"))+
  facet_grid(experimental.group ~ country,  margins=TRUE, scale="free") + 
  theme_tufte() +
  theme(legend.position = "none", axis.title = element_blank())
```

<br>

**Correlation matrix**

```{r}
pooled.credibility <-pooled %>% 
  select(credibility.item1:credibility.item6, country)

pooled.credibility %>% select(-country) %>%
  tab_corr(triangle="lower",
           remove.spaces=T,
           p.numeric = T,
           fade.ns = T,
           digits = 2,
           na.deletion="pairwise",
           title = "Correlation matrix: items of policy credibility scale",
           var.labels = str_c("Item ",1:6))
```

<br>

```{r include=FALSE}
factor.1.cfa <- 'policy.credibility  =~ credibility.item1 + credibility.item2.reversed + credibility.item3.reversed + credibility.item4 + credibility.item5 + credibility.item6'

factor.3.cfa.base <- 'non.interference  =~ credibility.item1 + credibility.item2.reversed + credibility.item3.reversed
expert.based =~ credibility.item4 + credibility.item5
stability   =~ credibility.item6'

factor.3.cfa.adjusted <- paste0(factor.3.cfa.base,
"\n",
"credibility.item2.reversed	~~	credibility.item3.reversed")

factor.3.cfa.alternative <- 'non.interference  =~ credibility.item2.reversed + credibility.item3.reversed
expert.based =~ credibility.item1 + credibility.item4 + credibility.item5 
stability   =~ credibility.item6'
```


# Conformitory factor analysis

We conducted our confirmatory factor analysis using `R lavaan` package.

<br>

## One-factor model:

**Model summary**
```{r,echo = TRUE}
fit.1factor <- cfa(factor.1.cfa, 
           std.lv=TRUE,  
           missing="fiml",  
           data=pooled.credibility)

summary(fit.1factor,fit.measures=T,standardize=T)
```

<br>

**Visualization of the model**
```{r}
semPaths(fit.1factor, "std", weighted = FALSE, nCharNodes = 7, shapeMan = "rectangle",
         sizeMan = 8,  intercepts = FALSE, edge.label.cex = 1, curvePivot = TRUE) 
```

<br > 

## Three-factors model: base

**Model summary**
```{r,echo = TRUE}
fit.3factors.base <- cfa(factor.3.cfa.base, 
           std.lv=TRUE,  
           missing="fiml",  
           data=pooled.credibility)

summary(fit.3factors.base, fit.measures=T,standardize=T)
```

<br>

**Visualization of the model**
```{r}
semPaths(fit.3factors.base, "std", weighted = FALSE, nCharNodes = 7, shapeMan = "rectangle",
         sizeMan = 8,  intercepts = FALSE, edge.label.cex = 1, curvePivot = TRUE) 
```

<br > 

**Modification indices**
```{r}
fit.improve.base <- modificationindices(fit.3factors.base, standardized =TRUE)

fit.improve.base %>%
  as_tibble() %>%
  slice_max(mi, n = 10) %>%
  arrange(-mi) %>% 
  select( 'Left hand side' = lhs, Operator = op, 'Right hand side' = rhs, 'Modification index' = mi,  'Expected parameter change'= epc) %>%
  kable(digits = 3) %>% 
    kable_styling(bootstrap_options = c("condensed",  "striped", "hover"),
                full_width = F,
                position = "left")
```

<br>

**Key parameters**
```{r}
parameterEstimates(fit.3factors.base, standardized=TRUE) %>% 
  filter(op == "=~") %>% 
  select('Latent Factor'=lhs, Indicator=rhs, B=est, SE=se, Z=z, 'p-value'=pvalue, Beta=std.all) %>% 
  mutate(Indicator = c(str_c("Item ",1:6))) %>% 
  kable(digits = 3) %>% 
    kable_styling(bootstrap_options = c("condensed"),
                full_width = F,
                position = "left")%>%
  collapse_rows(columns = 1, valign = "top")
```

## Three-factors model - adjusted:

**Model summary**
```{r,echo = TRUE}
fit.3factors.adjusted <- cfa(factor.3.cfa.adjusted, 
           std.lv=TRUE,  
           missing="fiml",  
           data=pooled.credibility)

summary(fit.3factors.adjusted, fit.measures=T, standardize=T)
```

<br >

**Visualization of the model**
```{r}
semPaths(fit.3factors.adjusted, "std", weighted = FALSE, nCharNodes = 7, shapeMan = "rectangle",
         sizeMan = 8,  intercepts = FALSE, edge.label.cex = 1, curvePivot = TRUE) 
```

<br >

**Modification indices**
```{r}
fit.improve.adjusted <- modificationindices(fit.3factors.adjusted)

fit.improve.adjusted %>%
  as_tibble() %>%
  slice_max(mi, n = 10) %>%
  arrange(-mi) %>% 
  select( 'Left hand side' = lhs, Operator = op, 'Right hand side' = rhs, 'Modification index' = mi,  'Expected parameter change'= epc) %>%
  kable(digits = 3) %>% 
    kable_styling(bootstrap_options = c("condensed",  "striped", "hover"),
                full_width = F,
                position = "left")
```

<br>

Judging this table,  it seems that item 1 may be better assigned to the 'expert.based' factor, rather than the 'non-interference' factor. Also, note the very high correlation between non-interference and expert-based.

<br>

**Key parameters**
```{r}
parameterEstimates(fit.3factors.adjusted, standardized=TRUE) %>% 
  filter(op == "=~") %>% 
  select('Latent Factor'=lhs, Indicator=rhs, B=est, SE=se, Z=z, 'p-value'=pvalue, Beta=std.all) %>% 
  mutate(Indicator = c(str_c("Item ",1:6))) %>% 
  kable(digits = 3) %>% 
    kable_styling(bootstrap_options = c("condensed"),
                full_width = F,
                position = "left")%>%
  collapse_rows(columns = 1, valign = "top")
```

## Three-factors model - alternative 

**Model summary**
```{r message=TRUE, warning=TRUE, include=FALSE}
fit.3factors.alternative <- cfa(factor.3.cfa.alternative, 
           std.lv=TRUE,  
           missing="fiml",  
           data=pooled.credibility)

summary(fit.3factors.alternative, standardize=T, fit.measures=T)
```

<br > 

**Visualization of the model**
```{r message=TRUE, warning=TRUE, paged.print=FALSE}
semPaths(fit.3factors.alternative, "std", weighted = FALSE, nCharNodes = 7, shapeMan = "rectangle",
         sizeMan = 8,  intercepts = FALSE, edge.label.cex = 1, curvePivot = TRUE) 
```

<br > 

**Modification indices**
```{r}
fit.improve.alternative <- modificationindices(fit.3factors.alternative)

fit.improve.alternative %>%
  as_tibble() %>%
  slice_max(mi, n = 10) %>%
  arrange(-mi) %>% 
  select( 'Left hand side' = lhs, Operator = op, 'Right hand side' = rhs, 'Modification index' = mi,  'Expected parameter change'= epc) %>%
  kable(digits = 3) %>% 
    kable_styling(bootstrap_options = c("condensed",  "striped", "hover"),
                full_width = F,
                position = "left")
```

< br>

**Factor loading**
```{r}
parameterEstimates(fit.3factors.alternative, standardized=TRUE) %>% 
  filter(op == "=~")  %>% 
 select('Latent Factor'=lhs, Indicator=rhs, B=est, SE=se, Z=z, 'p-value'=pvalue, Beta=std.all) %>%  
  mutate(Indicator = c("Item 2", "Item 3", "Item 1", "Item 4", "Item 5", "Item 6")) %>% 
  kable(digits = 3)%>% 
    kable_styling(bootstrap_options = c("condensed"),
                full_width = F,
                position = "left") %>%
  collapse_rows(columns = 1, valign = "top")
```

## Model comparison

**1 factor vs. 3 factors (base)**
```{r,echo = TRUE}
lavTestLRT(fit.3factors.base, fit.1factor)
```

**3 factors (base) vs. 3 factors (adjusted)**
```{r,echo = TRUE}
lavTestLRT(fit.3factors.base, fit.3factors.adjusted)
```

**1 factor vs. 3 factors (alternative)**
```{r}
lavTestLRT(fit.1factor, fit.3factors.alternative)
```

## Comparing models: A nice table 
```{r}
cfa.compare <- cbind(
m1 = inspect(fit.1factor, 'fit.measures'),
m2 =inspect(fit.3factors.base, 'fit.measures'),
m3= inspect(fit.3factors.adjusted, 'fit.measures'),
m4 =inspect(fit.3factors.alternative, 'fit.measures'))

cfa.compare  %>%
   t() %>%
   as_tibble() %>% 
   round(3) %>%
   unite("rmsea.ci", rmsea.ci.lower:rmsea.ci.upper, remove = FALSE, sep = " - ")  %>%
   select(Parameters = npar,
          "Chi-squared" = chisq,
          "Degrees of freedom" = df,
          "p-value" = pvalue,
          CFI = cfi,
          TLI = tli,
          AIC = aic,
          BIC = bic,
          RMSEA = rmsea,
          "RMSEA 95% CI" = rmsea.ci,
          "RMSEA < 0.05 p-value" = rmsea.pvalue) %>% 
   mutate(Model = c("Single factor",
                     "Baseline",
                     "Adjusted",
                     "Alternative")) %>% relocate(Model) %>%
  kable(booktabs = TRUE) %>% pack_rows(
  index = c("One factor" = 1, "Three Factors" = 3)) %>%  
    kable_styling(bootstrap_options = c("condensed",  "striped", "hover"),
                full_width = F,
                position = "left")
```

# Model per country:
```{r}
fit.final.country <- cfa(factor.3.cfa.adjusted, 
           data=pooled.credibility,
          std.lv=TRUE,  
           missing="fiml",
          group = "country")

summary(fit.final.country, standardize=T, fit.measures=T)

```

<br > 

**Visualization of the model**
```{r message=TRUE, warning=TRUE, paged.print=FALSE}
semPaths(fit.final.country, "std",ask=FALSE, weighted = FALSE, nCharNodes = 7, shapeMan = "rectangle",
         sizeMan = 8,  intercepts = FALSE, edge.label.cex = 1, curvePivot = TRUE, title = TRUE) 
# I couldn't figure out which model corresponds to which country. 
```

<br > 

**Modification indices**
```{r}
invariance <- measEq.syntax(configural.model = factor.3.cfa.adjusted, 
                      data = pooled.credibility, 
                      ordered = c("credibility.item1", "credibility.item2.reversed", "credibility.item3.reversed", "credibility.item4", "credibility.item5", "credibility.item6"),
                      parameterization = "theta",
                      ID.fac = "std.lv",
                      ID.cat = "Wu.Estabrook.2016",
                      group = "country",
                      group.equal = "configural")

invariance.model <- as.character(invariance)

invaraince.fit <- cfa(invariance.model,
                    data = pooled.credibility,
                    group = "country",
                     ordered = c("credibility.item1",
                                 "credibility.item2.reversed",
                                 "credibility.item3.reversed",
                                 "credibility.item4",
                                 "credibility.item5",
                                 "credibility.item6"))

summary(invaraince.fit)

# 'MeasE1.syntax' is the successor of the now deprecated function 'measurementInvariance'. It can be used to analyze (in)variance between groups: https://lavaan.ugent.be/tutorial/groups.html.

# However, the current code gives a warning and the output seems incorrect.

# See for instructions: https://towardsdatascience.com/measurement-invariance-definition-and-example-in-r-15b4efcab351
```

< br>

**Factor loading**
```{r}
parameterEstimates(fit.final.country, standardized=TRUE) %>% 
  filter(op == "=~")  %>% 
 select('Latent Factor'=lhs, Indicator=rhs, B=est, SE=se, Z=z, 'p-value'=pvalue, Beta=std.all, Country = group) %>%  
     relocate(Country) %>%
  kable(digits = 3) %>% 
    kable_styling(bootstrap_options = c("condensed","striped", "hover"),
                full_width = F,
                position = "left")
```


# Trust in EU institutions

## Distribution of items 

<br >

Trust in the European Parliament

```{r}
pooled %>%
  ggplot(aes(x=trust.EP, fill = experimental.group)) +
  geom_bar(width = 0.75,alpha=0.8)+
  scale_x_continuous(name="",limits = c(0,8),breaks = 1:7)+
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue2","dodgerblue3", "dodgerblue4"))+
  facet_grid(experimental.group ~ country,  margins=TRUE, scale="free") + 
  theme_tufte() +
  theme(legend.position = "none", axis.title = element_blank())
```

<br>

Trust in the European Commission

```{r}
pooled %>%
  ggplot(aes(x=trust.EC, fill = experimental.group)) +
  geom_bar(width = 0.75,alpha=0.8)+
  scale_x_continuous(name="",limits = c(0,8),breaks = 1:7)+
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue2","dodgerblue3", "dodgerblue4"))+
  facet_grid(experimental.group ~ country,  margins=TRUE, scale="free") + 
  theme_tufte() +
  theme(legend.position = "none", axis.title = element_blank())
```

<br>

Trust in the Council of the EU

```{r}
pooled %>%
  ggplot(aes(x=trust.council, fill = experimental.group)) +
  geom_bar(width = 0.75,alpha=0.8)+
  scale_x_continuous(name="",limits = c(0,8),breaks = 1:7)+
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue2","dodgerblue3", "dodgerblue4"))+
  facet_grid(experimental.group ~ country,  margins=TRUE, scale="free") + 
  theme_tufte() +
  theme(legend.position = "none", axis.title = element_blank())
```

## Correlation matrix
```{r}
pooled.trust <- pooled %>% 
  select(trust.EP, trust.EC, trust.council)

pooled.trust %>% 
  tab_corr(triangle="lower",
           remove.spaces=T,
           p.numeric = T,
           fade.ns = T,
           digits = 2,
           na.deletion="pairwise",
           title = "Correlation matrix: Trust in EU institutions",
           var.labels = c("European Parliament", "European Commission", "Council of the EU"))
```

## Reliability indices
```{r}
library(psych)
alpha.trust <- alpha(pooled.trust)[[1]]
alpha.trust %>% select(-c(average_r, median_r, `S/N`, ase)) %>% kable(col.names = c("Raw alpha",
                       "Standarized alpha",
                      "Guttman's Lambda 6",
                      "Mean of trust in EU institutions",
                      "SD of trust in EU institutions")) %>% 
    kable_styling(bootstrap_options = c("condensed", "striped", "hover"),
                full_width = F,
                position = "left")
```

# Summary statistics
```{r,results="asis", echo=FALSE,warning=FALSE,message=FALSE}
q1 <- pooled %>% 
  select(expertise,
         stability,
         noninterference,
         credibility.index,
         perceived.independence.reversed,
         intent.vaccine,
         
         trust.EU.institutions,
         trust.scientist,
         trust.politicians,
         trust.media,
         political.ideology,
         EU.integration,
         interpersonal.trust,
         familiarity.EMA,
         familiarity.advice,
         credibility.EMA.pre,
         credibility.EMA.post,
         trust.health.authorities,
         consequences.health,
         consequences.economic,
         importance.EMA.recoded,
         importance.FDA.recoded,
         importance.NRA.recoded,
         private.providers,
         knowledge,
         benefits.vaccines,
         
         independence,
         advice,
         no.text,
         
         female,
         healthcare,
         age) %>% 
  descr() %>% 
  data.frame() %>% 
  select(-type,
         -label,
         -se,
         -iqr,
         -trimmed,) %>% 
mutate_at(vars(c("NA.prc","mean","sd","md", "skew")),funs(round(.,3))) %>%
  mutate(var = c(
"1. Credibility (expertise)",
"2. Credibility (stability)",
"3. Credibility (non-interference)",
"4. Credibility.index",
"5. Perceived political independence",
"6. Vaccination intention",
"7. Trust in EU institutions",
"8. Trust in scientists",
"9. Trust in politicians",
"10. Trust in the media",
"11. Political ideology (left-right)",
"12. Support for EU integration",
"13. Interpersonal trust",
"14. Familiarity with EMA",
"15. FAmiliarity with EMA's opinion",
"16. Crebility of EMA (pre-manipulation)",
"17. Crebility of EMA (post-manipulation)",
"18. Trust in public health authorities",
"19. Consequences of coronacrisis for health",
"20. Consequences of coronacrisis for income",
"21. Importance of EMA's opinion",
"22. Importance of other regulators' opinion (e.g., FDA)",
"23. Importance of NRA's opinion",
"24. Believe in private markets",
"25. Knowledge of coronacrisis",
"26. Benefits of vaccines",
"27. Independence condition",
"28. Advice condition",
"29. No text condtion",
"30. Gender (Female = 1)",
"31. Works in healthcare",
"32. Age"))
rownames(q1) <- 1:nrow(q1)

q1 %>% 
  kable(col.names = c("Variable",
                       "n",
                      "% missing",
                      "Mean",
                      "SD",
                      "Median",
                      "Range",
                      "Skew")) %>% 
    kable_styling(bootstrap_options = c("condensed", "striped", "hover"),
                full_width = F,
                position = "left")
```

<br>

```{r}
pooled %>% 
  select(expertise,
         stability,
         noninterference,
         credibility.index,
         perceived.independence.reversed,
         intent.vaccine,
         
         trust.EU.institutions,
         trust.scientist,
         trust.politicians,
         trust.media,
         political.ideology,
         EU.integration,
         interpersonal.trust,
         familiarity.EMA,
         familiarity.advice,
         credibility.EMA.pre,
         credibility.EMA.post,
         trust.health.authorities,
         consequences.health,
         consequences.economic,
         importance.EMA,
         importance.FDA ,
         importance.NRA,
         private.providers,
         knowledge,
         benefits.vaccines,
         independence,
         advice,
         
          female,
          healthcare,
         age) %>% 
  tab_corr(triangle="lower",
           remove.spaces=T,
           p.numeric = T,
           show.p = T,
           fade.ns = F,
           digits = 2,
           na.deletion="pairwise",
           var.labels = str_c("Variable ", c(1:28,30:32)))
```

<br>

Note that I removed variable 29 ("no text") from the correlation plot as it gives an error during computation.

# Experiment: Perceived independence of EMA

<br>

## Randomisation check
This table shows how many respondents are assigned to each experimental group.
```{r}
pooled %>%
  group_by(experimental.group) %>%
  tally() %>%
  kable(col.names = c("Experimental group", "n")) %>%
    kable_styling(bootstrap_options = c("condensed", "striped", "hover"),
                full_width = F,
                position = "left") 
```

<br>

## Histogram
```{r}
pooled %>%
  ggplot(aes(x = perceived.independence.reversed, fill = experimental.group)) +
  geom_bar(width = 0.9, position = position_dodge()) + scale_y_continuous(name="") +
  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Independence group") +  scale_fill_viridis_d(name = "Independence group") + facet_grid(~country, margins = T) + theme_tufte() + theme(strip.text = element_text(hjust = 0, face = "bold"),
    legend.position="bottom",
    aspect.ratio = 2.5)
```

<br>

## T-test

```{r}
ggarrange(pooled  %>% ggplot(aes(x = experimental.group, y = perceived.independence.reversed, color = experimental.group)) +
      stat_summary(fun.data = mean_cl_normal, geom = "errorbar", alpha = 0.5, width = 0.1, size = 1, position = position_dodge(0.5)) + labs(color ='Experimental group', x = "", y = "", title = "Complete dataset") +
    stat_summary(fun = mean, geom = "point", alpha = 0.5, size = 2 , position = position_dodge(0.5)) +  facet_grid(.~country, margins = TRUE) +  theme_tufte() + theme(axis.text.x = element_blank(), axis.ticks = element_blank()),
    
    pooled %>% filter(comprehension.check.failed == "passed") %>% ggplot(aes(x = experimental.group, y = perceived.independence.reversed, color = experimental.group)) +
      stat_summary(fun.data = mean_cl_normal, geom = "errorbar", alpha = 0.5, width = 0.1, size = 1, position = position_dodge(0.5)) + labs(color ='Experimental group', x = "", y = "", title = "Only those who passed the comprehension check") +
    stat_summary(fun = mean, geom = "point", alpha = 0.5, size = 2 , position = position_dodge(0.5)) +  facet_grid(.~country, margins = TRUE) +  theme_tufte() + theme(axis.text.x = element_blank(), axis.ticks = element_blank()), nrow = 1, common.legend =  TRUE, legend = "bottom")
```

<br>

### With complete dataset (only advice/independence)
```{r}
tadaa_t.test(data = pooled.experiment, response = perceived.independence.reversed, group = experimental.group, print = "markdown")
```

<br>

### With those who failed the comprehension check filtered out (only advice/independence)
```{r}
tadaa_t.test(data = pooled.experiment, response = perceived.independence.reversed, group = experimental.group, print = "markdown")
```

<br>

### Anova?

# Time

<br>

```{r include=FALSE}
table.duration <- pooled %>%
  dplyr::summarize(mean = mean(duration),
            sd = sd(duration),
            min = min(duration),
            q1 = quantile(duration, probs = 0.25),
            median = median(duration),
            q3 = quantile(duration, probs = 0.75),
            max = max(duration)) %>% round(digits = 2)

table.intro.submit <- pooled %>% 
   dplyr::summarize(mean = mean(intro.submit),
            sd = sd(intro.submit),
            min = min(intro.submit),
            q1 = quantile(intro.submit, probs = 0.25),
            median = median(intro.submit),
            q3 = quantile(intro.submit, probs = 0.75),
            max = max(intro.submit)) %>% round(digits = 2)

table.manipulation.submit <- pooled %>% drop_na(manipulation.submit) %>% 
   dplyr::summarize(mean = mean(manipulation.submit),
            sd = sd(manipulation.submit),
            min = min(manipulation.submit),
            q1 = quantile(manipulation.submit, probs = 0.25),
            median = median(manipulation.submit),
            q3 = quantile(manipulation.submit, probs = 0.75),
            max = max(manipulation.submit)) %>% round(digits = 2)

table.decision.submit <- pooled %>% 
   dplyr::summarize(mean = mean(decision.submit),
            sd = sd(decision.submit),
            min = min(decision.submit),
            q1 = quantile(decision.submit, probs = 0.25),
            median = median(decision.submit),
            q3 = quantile(decision.submit, probs = 0.75),
            max = max(decision.submit)) %>% round(digits = 2)
```

<br>

## Survey duration

<br>

### Histogram
```{r}
pooled %>% filter(duration < 30) %>% 
plot_frq((duration),
        geom.colors = alpha("red",0.8),
        type = "hist",
        geom.size = 0.25) +
  theme(axis.text = element_text(face = "bold",  size= 9)) + labs(title = "Total survey duration") +  scale_x_continuous(name="Time in minutes", breaks = seq(0,30, 2)) +  scale_y_continuous(expand = expansion(c(0, 0.25))) + annotate(geom = "table", x = Inf, y = Inf, label = list(table.duration))
```

<br>

## Do participants read the information about the case?

<br>

### Page submission - introduction of case
```{r}
pooled %>% filter(intro.submit < 100) %>%  
plot_frq((intro.submit),
        geom.colors = scales::alpha("dodgerblue2",0.8),
        type = "hist",
        geom.size = 1) + 
  theme(axis.text = element_text(face = "bold",  size= 9)) +
  scale_x_continuous(name="Time in seconds",breaks = seq(0,100,5)) +   scale_y_continuous(expand = expansion(c(0, 0.1))) + annotate(geom = "table", x = Inf, y = Inf, label = list(table.intro.submit))
```

<br>

### Page submission - manipulation

<br>

*Histogram*
```{r}
pooled %>% filter(manipulation.submit < 100) %>%
plot_frq((manipulation.submit),
        geom.colors = scales::alpha("dodgerblue2",0.8),
        type = "hist",
        geom.size = 1) +
  theme(axis.text = element_text(face = "bold",  size= 9)) +
  scale_x_continuous(name="Time in seconds",breaks = seq(0,100,5)) +   scale_y_continuous(expand = expansion(c(0, 0.1))) + annotate(geom = "table", x = Inf, y = Inf, label = list(table.manipulation.submit))
```

<br>

*Broken down in quartiles per counry and total*
```{r}
t9 <- pooled.experiment  %>% ggplot(aes(x = manipulation.submit.quartile,y = perceived.independence.reversed, color = experimental.group)) +
      stat_summary(fun.data = mean_cl_normal, geom = "errorbar", alpha = 0.5, width = 0.1, size = 1, position = position_dodge(0.5)) + labs(color ='Experimental group', x = "Page submission - manipulation (quartiles)", y = "Perceived independence") +
    stat_summary(fun = mean, geom = "point", alpha = 0.5, size = 2 , position=position_dodge(0.5)) +  facet_grid(. ~ country, margins = TRUE) +  theme_tufte()
  
ggarrange(t9, common.legend = TRUE, legend = "bottom")
```

<br>

*Split dataset with 30 seconds as cut-off point*
```{r}
give.n <- function(x){
  return(c(y = mean(x)*1.15, label = length(x))) 
}

t10 <- pooled.experiment  %>% ggplot(aes(x = manipulation.submit.30,y = perceived.independence.reversed, color = experimental.group)) +
      stat_summary(fun.data = mean_cl_normal, geom = "errorbar", alpha = 0.5, width = 0.1, size = 1, position = position_dodge(0.25)) + labs(color ='Experimental group', x = "Page submission - manipulation", y = "Perceived independence") +
    stat_summary(fun = mean, geom = "point", alpha = 0.5, size = 2 , position=position_dodge(0.25)) +  facet_grid(. ~ country, margins = TRUE) +
  stat_summary(fun.data = give.n, geom = "text", fun = median, size = 4, col = "black") + theme_tufte()
  
ggarrange(t10, common.legend = TRUE, legend = "bottom")
```

### Page submission - EMA's decision
```{r}
pooled %>% filter(decision.submit < 100) %>% 
plot_frq((decision.submit),
        geom.colors = scales::alpha("dodgerblue2",0.8),
        type = "hist",
        geom.size = 1) + 
  theme(axis.text = element_text(face = "bold",  size= 9)) +
  scale_x_continuous(name= "Time in seconds", breaks = seq(0,100,5)) +   scale_y_continuous(expand = expansion(c(0, 0.1))) + annotate(geom = "table", x = Inf, y = Inf, label = list(table.decision.submit))
```

<br>

### Time and ...

<br>

***...Failing the comprehension check***

```{r}
t10 <- pooled.experiment %>% filter(duration < 30) %>% drop_na(comprehension.check.failed) %>%
  ggplot(aes(x= duration, color = comprehension.check.failed, fill = comprehension.check.failed)) + geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 2) +
 geom_density(alpha= .1, linetype= "dashed") + labs(title = "Total survey duration", x = "minutes") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

t11  <- pooled.experiment %>% filter(intro.submit < 60) %>% drop_na(comprehension.check.failed) %>% ggplot(aes(x= intro.submit, color = comprehension.check.failed, fill = comprehension.check.failed)) + geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 5) +
 geom_density(alpha= .1, linetype= "dashed") + labs(title = "Page submission - introduction", x = "seconds") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

t12 <- pooled.experiment %>% filter(manipulation.submit < 60) %>% drop_na(comprehension.check.failed) %>% ggplot(aes(x=manipulation.submit, color = comprehension.check.failed, fill = comprehension.check.failed)) + geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 5) + geom_density(alpha= .1, linetype= "dashed") + labs(title = "Page submission - manipulation", x = "seconds") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

t13 <- pooled.experiment %>% filter(decision.submit < 60) %>% drop_na(comprehension.check.failed) %>% ggplot(aes(x=decision.submit, color =comprehension.check.failed, fill = comprehension.check.failed)) + 
 geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 5) +
 geom_density(alpha= .1, linetype= "dashed") + labs(title = "Page submission - EMA's decision", x = "seconds") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

ggarrange(t10, t11, t12, t13, nrow = 2, ncol = 2, labels="AUTO", legend = "bottom", common.legend = TRUE)

# Change legend title
```

<br>

***...experimental groups***

```{r}
t14 <- pooled.experiment %>% filter(duration < 30) %>% ggplot(aes(x= duration, color = experimental.group, fill = experimental.group)) + geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 2) +
 geom_density(alpha= .1, linetype= "dashed") + labs(title = "Total survey duration", x = "minutes") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

t15  <- pooled.experiment %>% filter(intro.submit < 60) %>% ggplot(aes(x= intro.submit, color = experimental.group, fill = experimental.group)) + geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 5) +
 geom_density(alpha= .1, linetype= "dashed") + labs(title = "Page submission - introduction", x = "seconds") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

t16 <- pooled.experiment %>% filter(manipulation.submit < 60) %>% ggplot(aes(x=manipulation.submit, color = experimental.group, fill = experimental.group)) + geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 5) + geom_density(alpha= .1, linetype= "dashed") + labs(title = "Page submission - manipulation", x = "seconds") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

t17 <- pooled.experiment %>% filter(decision.submit < 60) %>% ggplot(aes(x=decision.submit, color = experimental.group, fill = experimental.group)) +
 geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 5) +
 geom_density(alpha= .1, linetype= "dashed") + labs(title = "Page submission - EMA's decision", x = "seconds", color = "Comprehension check") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

ggarrange(t14, t15, t16, t17, nrow = 2, ncol = 2, labels="AUTO", legend = "bottom", common.legend = TRUE)
```

<br>

To check if there is a significant difference in the time indicators, I ran four t-test. Note that I removed cases that were 1.5 times outside the inter-quartile range (iqr), as these cases can be considered outliers. However, this approach is contested and other strategies may be more appropiate here. 

<br > 

```{r include=FALSE}
out.duration <- boxplot(pooled.experiment$duration, plot=FALSE)$out
out.duration <-pooled.experiment[-which(pooled.experiment$duration %in% out.duration),]

out.intro.submit <- boxplot(pooled.experiment$intro.submit, plot=FALSE)$out
out.intro.submit <-pooled.experiment[-which(pooled.experiment$intro.submit %in% out.intro.submit),]

out.manipulation.submit <- boxplot(pooled.experiment$manipulation.submit, plot=FALSE)$out
out.manipulation.submit <-pooled.experiment[-which(pooled.experiment$manipulation.submit %in% out.manipulation.submit),]

out.decision.submit <- boxplot(pooled.experiment$decision.submit, plot=FALSE)$out
out.decision.submit <-pooled[-which(pooled.experiment$decision.submit %in% out.decision.submit),]
```

***Survey duration***
```{r}
tadaa_t.test(data = out.duration, response = duration, group = experimental.group, print = "markdown")
```

***Page submission - Introduction***
```{r}
tadaa_t.test(data = out.intro.submit, response = intro.submit, group = experimental.group, print = "markdown")
```

***Page submission - manipulation***
```{r}
tadaa_t.test(data = out.manipulation.submit, response = manipulation.submit, group = experimental.group, print = "markdown")
```

***Page submission - decision***
```{r}
tadaa_t.test(data = out.decision.submit, response = decision.submit, group = experimental.group, print = "markdown")
```

<br>

***...interface (pc/mobile)***

```{r}
t18 <- pooled %>% filter(duration < 30) %>% ggplot(aes(x= duration, color = device, fill = device)) + geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 2) +
 geom_density(alpha= .1, linetype= "dashed") + labs(title = "Total survey duration", x = "minutes") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

t19 <- pooled %>% filter(intro.submit < 60) %>% ggplot(aes(x= intro.submit, color = device, fill = device)) + geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 5) +
 geom_density(alpha= .1, linetype= "dashed") + labs(title = "Page submission - introduction", x = "seconds") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

t20 <- pooled %>% filter(manipulation.submit < 60) %>% ggplot(aes(x=manipulation.submit, color = device, fill = device)) + geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 5) + geom_density(alpha= .1, linetype= "dashed") + labs(title = "Page submission - manipulation", x = "seconds") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

t21 <- pooled %>% filter(decision.submit < 60) %>% ggplot(aes(x=decision.submit, color = device, fill = device)) +
 geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 5) +
 geom_density(alpha= .1, linetype= "dashed") + labs(title = "Page submission - EMA's decision", x = "seconds") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

ggarrange(t18, t19, t20, t21, nrow = 2, ncol = 2, labels="AUTO", legend = "bottom", common.legend = TRUE)
```

<br>



<br>

# Interface (mobile/pc)

<br>

## Distribution
```{r}
pooled %>%
  plot_frq(device,
        ylim = c(0,nrow(pooled)),
        geom.colors = scales::alpha("dodgerblue1",0.8))+
  theme_blank()
```

<br>

## Distribution of perceived independence for mobile/pc
```{r}
pooled %>%
  ggplot(aes(x = perceived.independence.reversed, fill = device)) + 
  geom_bar(width = 0.8, alpha = 1, position = position_dodge()) +  scale_x_continuous(name="Perceived independence", breaks = 1:7) + scale_y_continuous(name="") +  scale_fill_manual(name = "Device", values = c("dodgerblue2","dodgerblue4")) + facet_grid(~country, margins = TRUE) + theme_tufte() +  theme(legend.position="bottom")
```

<br>

```{r}
tadaa_t.test(data = pooled.experiment, response = perceived.independence.reversed, group = device, print = "markdown")
```

<br>

# Demography

## Age {.tabset}

### France
```{r}
age.population.FR <- read.csv("C:/Users/Thijs/surfdrive/COVID vaccine/git/FR/AGE_FR-08022021.csv")

age.population.FR <- age.population.FR %>% mutate(agecat = case_when(age < 25 ~ "younger than 25",
          age >= 25 & age < 30 ~ "25-29",
          age >= 30 & age < 35 ~ "30-34",
          age >= 35 & age < 40 ~ "35-39",
          age >= 40 & age < 45 ~ "40-44",
          age >= 45 & age < 50 ~ "45-49",
          age >= 50 & age < 55 ~ "50-54",
          age >= 55 & age < 60 ~ "55-59",
          age >= 60 & age < 65 ~ "60-64",
          age >= 65 & age < 70 ~ "65-69",
          age >= 70 & age < 75 ~ "70-74",
          age >= 75 & age < 80 ~ "75-79",
          age >= 80 ~ "80 or older"))
  
age.population.5.FR <- age.population.FR %>% group_by(agecat) %>% tally(count) %>% mutate(percentage = n / sum(n))

age.total.FR <- merge(age.population.5.FR, age.sample.FR, by.x = "agecat", by.y = "age.5")

age.total.FR <- age.total.FR %>% 
  rename(age.category = agecat,
  count.population = n.x,
  count.sample = n.y,
  percentage.population = percentage.x,
  percentage.sample = percentage.y)

age.total.FR$age.category <- factor(age.total.FR$age.category, levels = c(
"younger than 25",
"25-29",           "30-34",           "35-39",          
"40-44",           "45-49",           "50-54",          
"55-59",           "60-64",           "65-69",          
"70-74",           "75-79",           "80 or older"))    

age.total.FR %>% select(age.category, percentage.population, percentage.sample) %>% reshape2::melt(id.vars = 'age.category', variable.name = 'series')  %>% ggplot(aes(age.category, value, colour = series, fill = series)) + geom_bar (stat="identity", width=0.9, position = position_dodge(width=0.9)) + 
  theme_blank() + theme(legend.position="top", axis.text.x = element_text(angle = 45, hjust = 1), axis.title  = element_blank()) + scale_y_continuous(labels=scales::percent)
```

<br>

### Netherlands
```{r}
age.population.5.NL <- read.csv("C:/Users/Thijs/surfdrive/COVID vaccine/git/NL/AGE_POPULATION_SEGMENTS_NL-22012021.csv")

age.total.NL <- merge(age.population.5.NL, age.sample.NL, by.x = "誰..age", by.y = "age.5")

age.total.NL <- age.total.NL %>% 
  rename(age.category = 誰..age,
  count.population = count,
  count.sample = n,
  percentage.population = percentage.x,
  percentage.sample = percentage.y)

age.total.NL$age.category <- factor(age.total.NL$age.category, levels = c(
"younger than 25",
"25-29",           "30-34",           "35-39",          
"40-44",           "45-49",           "50-54",          
"55-59",           "60-64",           "65-69",          
"70-74",           "75-79",           "80 or older"))    

age.total.NL %>% select(age.category, percentage.population, percentage.sample) %>% reshape2::melt(id.vars = 'age.category', variable.name = 'series')  %>% ggplot(aes(age.category, value, colour = series, fill = series)) + geom_bar (stat="identity", width=0.9, position = position_dodge(width=0.9)) + 
  theme_blank() + theme(legend.position="top", axis.text.x = element_text(angle = 45, hjust = 1), axis.title  = element_blank()) + scale_y_continuous(labels=scales::percent)
```

### Ireland
```{r}

age.population.5.IE <- read.csv("C:/Users/Thijs/surfdrive/COVID vaccine/git/EN/AGE_POPULATION_SEGMENTS_EN_25012021.csv")

age.total.IE <- merge(age.population.5.IE, age.sample.IE, by.x = "誰..age", by.y = "age.5")

age.total.IE  <- age.total.IE  %>% 
  rename(age.category = 誰..age,
  count.population = count,
  count.sample = n,
  percentage.population = percentage.x,
  percentage.sample = percentage.y)

age.total.IE$age.category <- factor(age.total.IE$age.category, levels = c(
"younger than 25",
"25-29",           "30-34",           "35-39",          
"40-44",           "45-49",           "50-54",          
"55-59",           "60-64",           "65-69",          
"70-74",           "75-79",           "80 or older"))    

age.total.IE  %>% select(age.category, percentage.population, percentage.sample) %>% reshape2::melt(id.vars = 'age.category', variable.name = 'series')  %>% ggplot(aes(age.category, value, colour = series, fill = series)) + geom_bar (stat="identity", width=0.9, position = position_dodge(width=0.9)) + 
  theme_blank() + theme(legend.position="top", axis.text.x = element_text(angle = 45, hjust = 1), axis.title  = element_blank()) + scale_y_continuous(labels=scales::percent)
```

### Sweden
```{r}
age.population.5.SE <- read.csv("C:/Users/Thijs/surfdrive/COVID vaccine/git/SE/AGE_POPULATION_SEGMENTS_SE-22012021.csv")
age.total.SE <- merge(age.population.5.SE, age.sample.SE, by.x = "age", by.y = "age.5")

age.total.SE <- age.total.SE %>% 
  rename(age.category = age,
  count.population = count,
  count.sample = n,
  percentage.population = percentage.x,
  percentage.sample = percentage.y)

age.total.SE$age.category <- factor(age.total.SE$age.category, levels = c(
"younger than 25",
"25-29",           "30-34",           "35-39",          
"40-44",           "45-49",           "50-54",          
"55-59",           "60-64",           "65-69",          
"70-74",           "75-79",           "80 or older"))    

age.total.SE %>% select(age.category, percentage.population, percentage.sample) %>% reshape2::melt(id.vars = 'age.category', variable.name = 'series')  %>% ggplot(aes(age.category, value, colour = series, fill = series)) + geom_bar (stat="identity", width=0.9, position = position_dodge(width=0.9)) + 
  theme_blank() + theme(legend.position="top", axis.text.x = element_text(angle = 45, hjust = 1), axis.title  = element_blank()) + scale_y_continuous(labels=scales::percent)
```


## Gender
```{r}
pooled %>% 
plot_frq(female,
                ylim = c(0,nrow(pooled)),
        axis.labels = c("Male","Female"),
        title = "Gender")+ 
  theme_blank()
```

<br>

## Education



## Income


<br>

## Province

<br>

## Works in healthcare sector
```{r}
pooled %>% 
  plot_frq(healthcare,
        ylim = c(0,nrow(pooled)+500),
        title = "") + 
  theme_blank()
```

<br>

# Pre-post

## Distribution of credibility EMA (post)
```{r}
pooled %>% count(credibility.EMA.post) %>%  mutate(percentage = (n/(sum(n))*100) %>% round(2))  %>%
  adorn_totals("row") %>%  kable(col.names = c("Credibility EMA (post)", "n", "%")) %>% 

    kable_styling(bootstrap_options = c("condensed", "striped", "hover"),
                full_width = F,
                position = "left")
```

<br >

As this variable was added later to the survey, there is substantial missing data for this variable.

<br >

## Plot
```{r warning=TRUE}
t26 <- pooled  %>% 
  select(experimental.group,
         credibility.EMA.pre,
         credibility.EMA.post,
         country) %>% drop_na(credibility.EMA.post) %>%
  gather("key","value",-experimental.group, -country) %>% 
  mutate(key = recode(key,"'credibility.EMA.pre'='0.Pre';'credibility.EMA.post'='1.Post'"))
  
t26 %>% ggplot(aes(x=key,y=value,color=experimental.group))+
      stat_summary(fun.data = mean_cl_normal, geom = "errorbar", alpha=0.5,width=0.1,size=1,position=position_dodge(0.5)) + 
  stat_summary(fun = mean, geom = "point", alpha=0.5,size=2,position=position_dodge(0.5))+
  stat_summary(fun = mean, geom = "line", alpha=0.5,size=1,position=position_dodge(0.5), aes(group = experimental.group)) + labs(color ='Experimental group', x = "", y = "") + facet_grid(~country, margins = TRUE) +
  theme_tufte()
```

<br >

## Regression {.tabset}

### Total

**Models**
```{r}
prepost.total <- pooled %>% mutate(id = row_number()) %>% 
  select(experimental.group,
         id,
         credibility.EMA.pre,
         credibility.EMA.post,
         country) %>%
  drop_na() %>%
  gather("key","value",-experimental.group,-id,-country) %>% 
  mutate(post = key %>% Recode("'credibility.EMA.pre'= 0;'credibility.EMA.post'=1"),
         credibility = value) 


m1 <- lmer(credibility ~ post + (1|id),
                       data = prepost.total)

m2 <- m1 %>% update(.~.+experimental.group) 


m3 <- m2 %>% update(.~. + post*experimental.group)


tab_model(m2, m3,
          show.ci = F,
          show.se = T,
          collapse.se = T,
          emph.p = F)
```

<br >

**Interaction effect**
```{r}
plot_model(m3, type = "int")
```

### Ireland

**Models**
```{r}
prepost.IE <- prepost.total %>% filter(country == "IE")

m5 <- lmer(credibility ~ post + (1|id), data = prepost.IE)

m6 <- m5 %>% update(.~.+experimental.group) 

m7 <- m6 %>% update(.~. + post*experimental.group)

tab_model(m6, m7,
          show.ci = F,
          show.se = T,
          collapse.se = T,
          emph.p = F)
```

<br > 

**Interaction effect**
```{r}
plot_model(m7, type = "int")
```

### Sweden
```{r}
prepost.SE <- prepost.total %>% filter(country == "SE")

m8 <- lmer(credibility ~ post + (1|id),
                       data = prepost.SE)

m9 <- m8 %>% update(.~.+ experimental.group) 

m10 <- m9 %>% update(.~. + post*experimental.group)

tab_model(m9, m10,
          show.ci = F,
          show.se = T,
          collapse.se = T,
          emph.p = F)
```

<br > 

**Interaction effect**
```{r}
plot_model(m10, type = "int")
```

### France

**Models**
```{r}
prepost.FR <- prepost.total %>% filter(country == "FR")

m11 <- lmer(credibility ~ post + (1|id),
                       data = prepost.FR)

m12 <- m11 %>% update(.~.+ experimental.group) 

m13 <- m12 %>% update(.~. + post*experimental.group)

tab_model(m12, m13,
          show.ci = F,
          show.se = T,
          collapse.se = T,
          emph.p = F)
```

<br > 

**Interaction effect**
```{r}
plot_model(m13, type = "int")
```

<br > 

# Explaining perceived political independence
```{r results='asis'}
pooled.regression <- pooled %>% drop_na(age)

r1.4<- lm(perceived.independence.reversed ~
         trust.EU.institutions + trust.EP, data = pooled)

r1.1 <- lm(perceived.independence.reversed ~
         trust.EU.institutions +
         trust.scientist +
         trust.politicians +
         political.ideology +
         EU.integration +
         interpersonal.trust +
         familiarity.EMA +
         familiarity.advice +
         credibility.EMA.pre +
         trust.health.authorities +
         consequences.health +
         consequences.economic +
         importance.EMA.recoded +
         importance.FDA.recoded +
         importance.NRA.recoded +
         private.providers +
         knowledge +
         benefits.vaccines +
         
         experimental.group + 
         
         female +
         healthcare +
         poly(age, 2) +
         country,
                    data = pooled.regression,
                    na.action = na.omit)

r1.2 <- update(r1.1, . ~ . + trust.media)


stargazer(r1.1,
  r1.2,
  
  type = "html",
  report = "vcsp",
  style = "apsr",
  omit.stat = c("ser", "f"),
  dep.var.labels = "Perceived political independence",
  initial.zero = FALSE,
  notes = "*Notes*: Table entries are non-standardized OLS-regression coefficients, with Standard errors in parentheses.",
  notes.append = FALSE
)
```

<br >

# Explaining Vaccination intention

## Distribution of variable
```{r}
pooled %>%
  ggplot(aes(intent.vaccine, group = country)) + 
          geom_bar(aes(y = ..prop..), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          labs(y = "relative frequencies", x = "Vaccination intention") +
          facet_grid(~country, margins = TRUE) + theme_light()


```

## Regression models
```{r}
reg.intent.vaccine1 <- glm(intent.vaccine.recoded ~ trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA.post + familiarity.EMA + familiarity.advice +  political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + age + healthcare + income,
                    data = pooled,
                    na.action = na.omit,
                    family = binomial(link = 'logit'))

reg.intent.vaccine2 <- glm(intent.vaccine.recoded ~ credibility.index + trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA.post + familiarity.EMA + familiarity.advice +  political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + age + healthcare + income,
                    data = pooled,
                    na.action = na.omit,
                    family = binomial(link = 'logit'))

reg.intent.vaccine3 <- glm(intent.vaccine.recoded ~ perceived.independence.reversed + trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA.post + familiarity.EMA + familiarity.advice +  political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + age + healthcare + income,
                    data = pooled,
                    na.action = na.omit,
                    family = binomial(link = 'logit'))

reg.intent.vaccine4 <- glm(intent.vaccine.recoded ~ credibility.index + perceived.independence.reversed + trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA.post + familiarity.EMA + familiarity.advice +  political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + age + healthcare + income,
                    data = pooled,
                    na.action = na.omit,
                    family = binomial(link = 'logit'))

tab_model(reg.intent.vaccine1, reg.intent.vaccine2, reg.intent.vaccine3, reg.intent.vaccine4, show.ci = FALSE)
```

<br>

# Explaning crebility of EMA's decision


## Stability

### Distribution of variable
```{r}
reg.credibility1 <- lm(credibility.index  ~ trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA.post + familiarity.EMA + familiarity.advice + political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + poly(age, 2) + healthcare + income,
                    data = pooled,
                    na.action = na.omit)

reg.credibility2 <- lm(credibility.index  ~ perceived.independence.reversed + trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA.post + familiarity.EMA + familiarity.advice +  political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + poly(age, 2) + healthcare + income,
                    data = pooled,
                    na.action = na.omit)

reg.credibility3 <- lm(credibility.index  ~ perceived.independence.reversed + trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA.post + familiarity.EMA +  + familiarity.advice +  political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + poly(age, 2) + healthcare + income + perceived.independence.reversed:benefits.vaccines + benefits.vaccines:experimental.group,
                    data = pooled,
                    na.action = na.omit)

reg.credibility4 <- lm(credibility.index  ~ perceived.independence.reversed + trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA.post + familiarity.EMA +  + familiarity.advice +  political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + age.recoded + healthcare + income + perceived.independence.reversed:benefits.vaccines + benefits.vaccines:experimental.group,
                    data = pooled,
                    na.action = na.omit)


reg.credibility3.centered <- meanCenter(reg.credibility3, centerOnlyInteractors = TRUE, centerDV = FALSE)

reg.credibility4.centered <- meanCenter(reg.credibility4, centerOnlyInteractors = TRUE, centerDV = FALSE)

tab_model(reg.credibility1, reg.credibility2, reg.credibility3.centered, show.ci = FALSE)
```

## Expertise

### Distribution of variable

## Non-interference

### Distribution of variable

## Crebility index

### Distribution of variable


<br>


### Plots

***Interaction effect: perceived independence x benefits of vaccines***
```{r}
plot_model(reg.credibility3.centered, type = "int", mdrt.values = "meansd")[[1]]
```

***Interaction effect: perceived independence x experimental group***
```{r}
plot_model(reg.credibility3.centered, type = "int", mdrt.values = "meansd")[[2]]
```

***marginal effects: Effect of perceived independence on credibility for different age groups***
```{r}
plot_model(reg.credibility4.centered, type = "pred", terms = c("perceived.independence.reversedc", "age.recoded"))
```




<br>

# Remarks from participants

## General
```{r}
df.total %>% 
  filter(nchar(comments.general)>1) %>% 
  select(comments.general) %>% 
  kable() %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%    scroll_box(height = "400px")
```

## Vaccination intention
```{r}
pooled %>% 
  filter(nchar(Q16.3)>1) %>% 
  select(Q16.3) %>% 
  kable() %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%    scroll_box(height = "400px")
```
