---
title: "REPORT CONTROL CHECK  V201"
author: "Thijs de Boer"
date: "2021"
output:
  html_document:
    code_folding: hide
    fig_captions: yes
    highlight: haddock
    number_sections: yes
    theme: flatly
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
      toc_depth: 3
---


Last update: `r Sys.time()`

```{r set-global-options, echo = FALSE}
knitr::opts_chunk$set(eval = TRUE, 
                      echo = TRUE, 
                      message=FALSE,
                      warning = FALSE,
                      cache = FALSE,
                      include = TRUE,
                      collapse = FALSE,
                      dependson = NULL,
                      engine = "R", #  Chunks will always have R code, unless noted
                      error = TRUE,
                      fig.path="Figures/",  #  Set the figure options
                      fig.align = "left",
                      fig.width = 6,
                      fig.height = 4)
```

```{r silent-packages, echo = FALSE, eval = TRUE, message=FALSE, include = FALSE}
library(sjPlot)
library(sjstats)
library(tidyverse)
library(car)
library(ggthemes)
library(kableExtra)
library(lme4)
library(ggpubr)
library(scales)
library(ggpmisc)
library(tadaatoolbox)
library(data.table)
library(psych)
```

```{r}
load("C:/Users/Thijs/surfdrive/COVID vaccine/git/Control/NL - control check/.RData")
load("C:/Users/Thijs/surfdrive/COVID vaccine/git/Control/SE - control check/.RData")

df.def.error <- dplyr::bind_rows(df.def.NL, df.def.SE)

df.def.error <- df.def.error %>% mutate(duration.quartile = case_when(
  duration <= quantile(duration, probs = 0.25) ~ "Q1",
  duration > quantile(duration, probs = 0.25) & duration <= quantile(duration, probs = 0.5)  ~ "Q2",
  duration > quantile(duration, probs = 0.5) & duration <= quantile(duration, probs = 0.75)  ~ "Q3",
  duration > quantile(duration, probs = 0.75) ~ "Q4"))

df.def.error <- df.def.error %>% mutate(intro.submit.recoded = case_when(
  intro.submit < quantile(intro.submit, probs = 0.5) ~ "< median",
    intro.submit > quantile(intro.submit, probs = 0.5) ~ "> median"))

df.def.error$duration.quartile <- factor(df.def.error$duration.quartile, levels = c("Q1", "Q2", "Q3", "Q4"))

df.def.error$experimental.group <- factor(df.def.error$experimental.group, levels = c("no text", "advice", "independence"))

df.def.error.NL$experimental.group <- factor(df.def.error.NL$experimental.group, levels = c("no text", "advice"))
df.def.NL$experimental.group <- factor(df.def.NL$experimental.group, levels = c("no text", "advice"))
df.check.NL$experimental.group <- factor(df.check.NL$experimental.group, levels = c("no text", "advice"))
df.def.SE$experimental.group <- factor(df.def.SE$experimental.group, levels = c("no text", "advice", "independence"))
df.check.SE$experimental.group <- factor(df.check.SE$experimental.group, levels = c("no text", "advice", "independence"))

df.check <- dplyr::bind_rows(df.check.NL, df.check.SE)
df.total <- dplyr::bind_rows(df.total.NL, df.total.SE)
df.intro <- df.def.error %>% filter(intro.submit.recoded == "> median")
df.intro.NL <- df.intro %>% filter(country == "NL")
df.intro.SE <- df.intro %>% filter(country == "SE")

set_theme(
  base=theme_blank(),
  geom.outline.size = 0.01,
  geom.outline.color = "white", 
  geom.label.size = 3,
  geom.label.color = "grey50")
```

# Population

Total number of participants:
```{r}
df.total %>% nrow()
```

Number of participants that failed the attention test:
```{r}
df.total %>% nrow() - df.total %>% filter(IMC=="1") %>% nrow()
```

Participants between 0-17:
```{r}
df.total %>% filter(IMC=="1" & age < 18) %>% nrow()
```

Percentage of participants who are at least 18 years old and did not fail the IMC:
```{r}
percent(df.def.error %>% nrow() / df.total  %>% nrow())
```

Number of participants in this analysis:
```{r}
df.def.error %>% nrow()
```

Number of participants in the final dataset that failed the manipulation check:
```{r}
df.def.error %>% nrow() - df.def.error %>% filter(manipulation.check=="1") %>% nrow()
```

Which is:
```{r}
percent(df.def.error %>% filter(manipulation.check!="1") %>% nrow() / df.def.error %>% nrow(), accuracy = 0.01)
```

<br>

# Experiment: Perceived independence of EMA

<br>

## Randomisation check
This table shows how many respondents are assigned to each experimental group.
```{r}
df.def.error %>%
  group_by(experimental.group) %>%
  tally()
```

<br>

## Full dataset

### Description
```{r}
df.def.error %>% 
sjmisc::descr(perceived.independence.reversed, show = c("n", "NA.prc", "mean", "sd", "md", "iqr", "trimmed", "range", "skew")) %>%
  kbl(digits= 2) %>%
 kable_paper()
```

<br>

### Histogram
```{r}
ggarrange(df.def.error %>%
  ggplot(aes(x = perceived.independence.reversed, fill = experimental.group)) +
  geom_bar(width = 0.75,alpha = 0.8, position = position_dodge()) + labs(y = "", title = "Total") +
  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
  
  df.def.error.NL  %>% 
  ggplot(aes(x = perceived.independence.reversed, fill = experimental.group)) +
  geom_bar(width = 0.75,alpha = 0.8, position = position_dodge()) + labs(y = "", title = "NL") +
  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
  
   df.def.SE %>% 
  ggplot(aes(x = perceived.independence.reversed, fill = experimental.group)) +
  geom_bar(width = 0.75,alpha = 0.8, position = position_dodge()) + labs(y = "", title = "Sweden") +
  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
  
  ncol = 3, common.legend = TRUE)
  
```

<br>

### Statistics

<br>

**Regression**
```{r}
reg.perceived.independence.total <- lm(perceived.independence.reversed ~  experimental.group,
                    data = df.def.error,
                    na.action = na.omit)

reg.perceived.independence.SE <- lm(perceived.independence.reversed ~ experimental.group,
                    data = df.def.SE,
                    na.action = na.omit)

reg.perceived.independence.NL <- lm(perceived.independence.reversed ~  experimental.group,
                    data = df.def.error.NL,
                    na.action = na.omit)

tab_model(reg.perceived.independence.total, reg.perceived.independence.SE, reg.perceived.independence.NL, dv.labels = c("Perceived independence - Total", "Perceived independence - SE", "Perceived independence - NL"), title = "Perceived independence - no filter", show.ci = FALSE)
```

<br>

**Total**
```{r}
tadaa_aov(perceived.independence.reversed ~ experimental.group, data = df.def.error, print = "markdown")
```

<br>

**Sweden**
```{r}
tadaa_aov(perceived.independence.reversed ~ experimental.group, data = df.def.SE, print = "markdown")
```

<br>

**Netherlands**
```{r}
tadaa_t.test(data = df.def.error.NL, response = perceived.independence.reversed, group = experimental.group, print = "markdown")
```

<br>

### Histogram
```{r}
ggarrange(df.check %>%
  ggplot(aes(x = perceived.independence.reversed, fill = experimental.group)) +
  geom_bar(width = 0.75,alpha = 0.8, position = position_dodge()) + labs(y = "", title = "Total") +
  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
  
  df.check.NL %>% 
  ggplot(aes(x = perceived.independence.reversed, fill = experimental.group)) +
  geom_bar(width = 0.75,alpha = 0.8, position = position_dodge()) + labs(y = "", title = "NL") +
  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
  
    df.check.SE %>% 
  ggplot(aes(x = perceived.independence.reversed, fill = experimental.group)) +
  geom_bar(width = 0.75,alpha = 0.8, position = position_dodge()) + labs(y = "", title = "Sweden") +
  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
  
  ncol = 3, common.legend = TRUE)
  
```

### Statistics

<br>

**Regression**
```{r}
reg.perceived.independence.total.check <- lm(perceived.independence.reversed ~  experimental.group,
                    data = df.check,
                    na.action = na.omit)

reg.perceived.independence.SE.check <- lm(perceived.independence.reversed ~ experimental.group,
                    data = df.check.SE,
                    na.action = na.omit)

reg.perceived.independence.NL.check <- lm(perceived.independence.reversed ~  experimental.group,
                    data = df.check.NL,
                    na.action = na.omit)

tab_model(reg.perceived.independence.total.check, reg.perceived.independence.SE.check, reg.perceived.independence.NL.check, dv.labels = c("Perceived independence - Total", "Perceived independence - SE", "Perceived independence - NL"), title = "Perceived independence - filter: manipulation check", show.ci = FALSE)
```

<br>

**Total**
```{r}
tadaa_aov(perceived.independence.reversed ~ experimental.group, data = df.check, print = "markdown")
```

<br>

**Sweden**
```{r}
tadaa_aov(perceived.independence.reversed ~ experimental.group, data = df.check.SE, print = "markdown")
```

<br>

**Netherlands**
```{r}
tadaa_t.test(data = df.check.NL, response = perceived.independence.reversed, group = experimental.group, print = "markdown")
```

## Only those who spent more time on the introduction page of the case than the median participant

### Description
```{r}
df.intro %>%  
sjmisc::descr(perceived.independence.reversed, show = c("n", "NA.prc", "mean", "sd", "md", "iqr", "trimmed", "range", "skew")) %>%
  kbl(digits= 2) %>%
 kable_paper()
```

### Histogram
```{r}
ggarrange(df.intro %>%
  ggplot(aes(x = perceived.independence.reversed, fill = experimental.group)) +
  geom_bar(width = 0.75,alpha = 0.8, position = position_dodge()) + labs(y = "", title = "Total") +
  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
  
  df.intro.NL   %>%
  ggplot(aes(x = perceived.independence.reversed, fill = experimental.group)) +
  geom_bar(width = 0.75,alpha = 0.8, position = position_dodge()) + labs(y = "", title = "NL") +
  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
  
 df.intro.SE  %>%
  ggplot(aes(x = perceived.independence.reversed, fill = experimental.group)) +
  geom_bar(width = 0.75,alpha = 0.8, position = position_dodge()) + labs(y = "", title = "Sweden") +
  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
  
  ncol = 3, common.legend = TRUE)
  
```

### Statistics

<br>

**Regression**
```{r}
reg.perceived.independence.total.intro <- lm(perceived.independence.reversed ~  experimental.group,
                    data = df.intro,
                    na.action = na.omit)

reg.perceived.independence.SE.intro <- lm(perceived.independence.reversed ~ experimental.group,
                    data =  df.intro.SE,
                    na.action = na.omit)

reg.perceived.independence.NL.intro <- lm(perceived.independence.reversed ~  experimental.group,
                    data =   df.intro.NL,
                    na.action = na.omit)

tab_model(reg.perceived.independence.total.intro, reg.perceived.independence.SE.intro, reg.perceived.independence.NL.intro, dv.labels = c("Perceived independence - Total", "Perceived independence - SE", "Perceived independence - NL"), title = "Perceived independence - filter: introduction of case", show.ci = FALSE)
```

<br>

**Total**
```{r}
tadaa_aov(perceived.independence.reversed ~ experimental.group, data = df.intro, print = "markdown")
```

<br>

**Sweden**
```{r}
tadaa_aov(perceived.independence.reversed ~ experimental.group, data = df.intro.SE, print = "markdown")
```

<br>

**Netherlands**
```{r}
tadaa_t.test(data = df.intro, response = perceived.independence.reversed, group = experimental.group, print = "markdown")
```

# Credbility

## Full dataset

### Description
```{r}
df.def.error %>% 
sjmisc::descr(credibility.index, show = c("n", "NA.prc", "mean", "sd", "md", "iqr", "trimmed", "range", "skew")) %>%
  kbl(digits= 2) %>%
 kable_paper()
```

### Histogram
```{r}
ggarrange(df.def.error %>% ggplot(aes(x= credibility.index, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title.y = element_blank()) + labs(y = "", title = "Total") +
  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
 df.def.error.NL
 %>% ggplot(aes(x= credibility.index, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title.y = element_blank()) + labs(y = "", title = "Netherlands") +
  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
  df.def.SE  %>% ggplot(aes(x= credibility.index, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title.y = element_blank()) + labs(y = "", title = "Sweden") +
  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
  ncol = 3, common.legend = TRUE)
 
```

### Statistics

<br>

**Regression**
```{r}
reg.credibility.total <- lm(credibility.index ~  experimental.group,
                    data = df.def.error,
                    na.action = na.omit)

reg.credibility.SE <- lm(credibility.index ~ experimental.group,
                    data =  df.def.SE,
                    na.action = na.omit)

reg.credibility.NL <- lm(credibility.index ~  experimental.group,
                    data =   df.def.error.NL,
                    na.action = na.omit)

tab_model(reg.credibility.total, reg.credibility.SE, reg.credibility.NL, dv.labels = c("Credibility - Total", "Credibility - SE", "Credibility - NL"), title = "Credibility - no filter", show.ci = FALSE)
```

<br>

**Total**
```{r}
tadaa_aov(credibility.index ~ experimental.group, data = df.def.error, print = "markdown")
```

<br>

**Sweden**
```{r}
tadaa_aov(credibility.index ~ experimental.group, data = df.def.SE, print = "markdown")
```

<br>

**Netherlands**
```{r}
tadaa_t.test(data = df.def.error.NL, response = credibility.index, group = experimental.group, print = "markdown")
```

<br >

## Filtering out those who failed the manipulation check 

Participants that received the erroneous manipulation check are filtered out as well.


### Description
```{r}
df.check %>%
sjmisc::descr(credibility.index, show = c("n", "NA.prc", "mean", "sd", "md", "iqr", "trimmed", "range", "skew")) %>%
  kbl(digits= 2) %>%
 kable_paper()
```

### Histogram
```{r}
ggarrange(df.check%>% ggplot(aes(x= credibility.index, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title.y = element_blank()) + labs(y = "", title = "Total") +
  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
 df.check.NL %>% ggplot(aes(x= credibility.index, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title.y = element_blank()) + labs(y = "", title = "Netherlands") +
  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
  df.check.SE %>% ggplot(aes(x= credibility.index, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title.y = element_blank()) + labs(y = "", title = "Sweden") +
  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
  ncol = 3, common.legend = TRUE)
 
```

### Statistics

<br>

**Regression**
```{r}
reg.credibility.total.check <- lm(credibility.index ~  experimental.group,
                    data = df.check,
                    na.action = na.omit)

reg.credibility.SE.check  <- lm(credibility.index ~ experimental.group,
                    data =  df.check.SE,
                    na.action = na.omit)

reg.credibility.NL.check <- lm(credibility.index ~  experimental.group,
                    data =   df.check.NL,
                    na.action = na.omit)

tab_model(reg.credibility.total.check, reg.credibility.SE.check, reg.credibility.NL.check, dv.labels = c("Credibility - Total", "Credibility - SE", "Credibility - NL"), title = "Credibility - filter: manipulation check", show.ci = FALSE)
```

<br>

**Total**
```{r}
tadaa_aov(credibility.index ~ experimental.group, data = df.check, print = "markdown")
```

<br>

**Sweden**
```{r}
tadaa_aov(credibility.index ~ experimental.group, data = df.check.SE, print = "markdown")
```

<br>

**Netherlands**
```{r}
tadaa_t.test(data = df.check.NL, response = credibility.index, group = experimental.group, print = "markdown")
```

## Only those who spent more time on the introduction page of the case than the median participant

### Description
```{r}
df.intro %>%
sjmisc::descr(credibility.index, show = c("n", "NA.prc", "mean", "sd", "md", "iqr", "trimmed", "range", "skew")) %>%
  kbl(digits= 2) %>%
 kable_paper()
```

### Histogram
```{r}
ggarrange(df.intro %>% ggplot(aes(x= credibility.index, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title.y = element_blank()) + labs(y = "", title = "Total") +
  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
  df.intro.NL %>% ggplot(aes(x= credibility.index, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title.y = element_blank()) + labs(y = "", title = "Netherlands") +
  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
  df.intro.SE %>%  ggplot(aes(x= credibility.index, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title.y = element_blank()) + labs(y = "", title = "Sweden") +
  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
  ncol = 3, common.legend = TRUE)
```

### Statistics

<br>

**Regression**
```{r}
reg.credibility.total.intro <- lm(credibility.index ~  experimental.group,
                    data = df.intro,
                    na.action = na.omit)

reg.credibility.SE.intro <- lm(credibility.index ~ experimental.group,
                    data =  df.intro.SE,
                    na.action = na.omit)

reg.credibility.NL.intro <- lm(credibility.index ~  experimental.group,
                    data =   df.intro.NL,
                    na.action = na.omit)

tab_model(reg.credibility.total.intro, reg.credibility.SE.intro, reg.credibility.NL.intro, dv.labels = c("Credibility - Total", "Perceived independence - SE", "Credibility - NL"), title = "Credibility - filter: introduction of case", show.ci = FALSE)
```

<br>

**Total**
```{r}
tadaa_aov(credibility.index ~ experimental.group, data = df.intro, print = "markdown")
```

<br>

**Sweden**
```{r}
tadaa_aov(credibility.index~ experimental.group, data = df.intro.SE, print = "markdown")
```

<br>

**Netherlands**
```{r}
tadaa_t.test(data = df.intro.NL, response = credibility.index, group = experimental.group, print = "markdown")
```

# Credibility dimensions



## Internal consistency

### Non-interference
```{r}
df.def.error %>% select(credibility.item1:credibility.item3.reversed) %>% psych::alpha() -> alpha.noninterference

alpha.noninterference$total %>%
  kbl(digits= 2, caption = "Cronbach's alpha: non-interference") %>%
 kable_paper()
```

<br>

### Expertise
```{r}
 df.def.error %>% select(credibility.item4,credibility.item5) %>% psych::alpha() -> alpha.expertise

alpha.expertise$total %>%
  kbl(digits= 2, caption = "Cronbach's alpha: expertise") %>%
 kable_paper()
```


## Description
```{r}
df.def.error %>% select(credibility.expert, credibility.noninterference, credibility.stability)  %>% 
sjmisc::descr(show = c("n", "NA.prc", "mean", "sd", "md", "iqr", "trimmed", "range", "skew")) %>%
  kbl(digits= 2) %>%
 kable_paper()
```


## Histogram
```{r}
ggarrange(df.def.error %>% ggplot(aes(x= credibility.expert, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Total: expertise") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
 df.def.error.NL %>% ggplot(aes(x= credibility.expert, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Netherlands: expertise") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
  df.def.SE %>% ggplot(aes(x= credibility.expert, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Sweden: expertise") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
 df.def.error %>% ggplot(aes(x= credibility.stability, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Total: stability") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
 df.def.error.NL %>% ggplot(aes(x= credibility.stability, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Netherlands: stability") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
  df.def.SE %>% ggplot(aes(x= credibility.stability, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Sweden: stability") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
 df.def.error %>% ggplot(aes(x= credibility.noninterference, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Total: non-interference") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
 df.def.error.NL %>% ggplot(aes(x= credibility.noninterference, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Netherlands: non-interference") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
  df.def.SE %>% ggplot(aes(x= credibility.noninterference, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Sweden: non-interference") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
  ncol = 3, nrow = 3, common.legend = TRUE)
```

<br>

## Statistics: full dataset

### Expertise

<br>

**Regression**
```{r}
reg.credibility.expertise.total <- lm(credibility.expert ~  experimental.group,
                    data = df.def.error,
                    na.action = na.omit)

reg.credibility.expertise.SE <- lm(credibility.expert ~ experimental.group,
                    data =  df.def.SE,
                    na.action = na.omit)

reg.credibility.NL <- lm(credibility.expert ~  experimental.group,
                    data =   df.def.error.NL,
                    na.action = na.omit)

tab_model(reg.credibility.expertise.total, reg.credibility.expertise.SE, reg.credibility.NL, dv.labels = c("Expertise - Total", "Expertise - SE", "Expertise - NL"), title = "Expertise - no filter", show.ci = FALSE)
```

<br>

**Total**
```{r}
tadaa_aov(credibility.expert ~ experimental.group, data = df.def.error, print = "markdown")
```

<br>

**Sweden**
```{r}
tadaa_aov(credibility.expert ~ experimental.group, data = df.def.SE, print = "markdown")
```

<br>

**Netherlands**
```{r}
tadaa_t.test(data = df.def.error.NL, response = credibility.expert, group = experimental.group, print = "markdown")
```

### Stability

<br>

**Regression**
```{r}
reg.credibility.stability.total <- lm(credibility.stability ~  experimental.group,
                    data = df.def.error,
                    na.action = na.omit)

reg.credibility.stability.SE <- lm(credibility.stability ~ experimental.group,
                    data =  df.def.SE,
                    na.action = na.omit)

reg.stability.NL <- lm(credibility.stability ~  experimental.group,
                    data =   df.def.error.NL,
                    na.action = na.omit)

tab_model(reg.credibility.stability.total, reg.credibility.stability.SE, reg.stability.NL, dv.labels = c("Stability - Total", "Stability - SE", "Stability - NL"), title = "Stability - no filter", show.ci = FALSE)
```

<br>

**Total**
```{r}
tadaa_aov(credibility.stability ~ experimental.group, data = df.def.error, print = "markdown")
```

<br>

**Sweden**
```{r}
tadaa_aov(credibility.stability ~ experimental.group, data = df.def.SE, print = "markdown")
```

<br>

**Netherlands**
```{r}
tadaa_t.test(data = df.def.error.NL, response = credibility.stability, group = experimental.group, print = "markdown")
```

### Non-interference

<br>

**Regression**
```{r}
reg.credibility.noninterference.total <- lm(credibility.noninterference ~  experimental.group,
                    data = df.def.error,
                    na.action = na.omit)

reg.credibility.noninterference.SE <- lm(credibility.noninterference ~ experimental.group,
                    data =  df.def.SE,
                    na.action = na.omit)

reg.noninterference.NL <- lm(credibility.noninterference ~  experimental.group,
                    data =   df.def.error.NL,
                    na.action = na.omit)

tab_model(reg.credibility.noninterference.total, reg.credibility.noninterference.SE, reg.noninterference.NL, dv.labels = c("Non-interference - Total", "Non-interference - SE", "Non-interference - NL"), title = "Non-interference - no filter", show.ci = FALSE)
```

<br>

**Total**
```{r}
tadaa_aov(credibility.noninterference ~ experimental.group, data = df.def.error, print = "markdown")
```

<br>

**Sweden**
```{r}
tadaa_aov(credibility.noninterference ~ experimental.group, data = df.def.SE, print = "markdown")
```

<br>

**Netherlands**
```{r}
tadaa_t.test(data = df.def.error.NL, response = credibility.noninterference, group = experimental.group, print = "markdown")
```

### Histograms
```{r}
ggarrange(df.check %>% ggplot(aes(x= credibility.expert, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Total: expertise") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
 df.check %>% filter(country == "NL") %>% ggplot(aes(x= credibility.expert, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Netherlands: expertise") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
  df.check %>% filter(country == "SE") %>% ggplot(aes(x= credibility.expert, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Sweden: expertise") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
 df.check %>% ggplot(aes(x= credibility.stability, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Total: stability") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
 df.check %>% filter(country == "NL") %>% ggplot(aes(x= credibility.stability, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Netherlands: stability") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
  df.check %>% filter(country == "SE") %>% ggplot(aes(x= credibility.stability, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Sweden: stability") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
 df.check %>% ggplot(aes(x= credibility.noninterference, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Total: non-interference") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
 df.check %>% filter(country == "NL") %>% ggplot(aes(x= credibility.noninterference, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Netherlands: non-interference") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
  df.check %>% filter(country == "SE") %>% ggplot(aes(x= credibility.noninterference, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Sweden: non-interference") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
  ncol = 3, nrow = 3, common.legend = TRUE)
```

### Expertise

<br>

**Regression**
```{r}
reg.credibility.expertise.total.check <- lm(credibility.expert ~  experimental.group,
                    data = df.check,
                    na.action = na.omit)

reg.credibility.expertise.SE.check <- lm(credibility.expert ~ experimental.group,
                    data =  df.check.SE,
                    na.action = na.omit)

reg.credibility.NL.check <- lm(credibility.expert ~  experimental.group,
                    data =   df.check.NL,
                    na.action = na.omit)

tab_model(reg.credibility.expertise.total.check, reg.credibility.expertise.SE.check, reg.credibility.NL.check, dv.labels = c("Expertise - Total", "Expertise - SE", "Expertise - NL"), title = "Expertise - filter: manipulation check", show.ci = FALSE)
```

<br>

**Total**
```{r}
tadaa_aov(credibility.expert ~ experimental.group, data = df.check, print = "markdown")
```

<br>

**Sweden**
```{r}
tadaa_aov(credibility.expert ~ experimental.group, data = df.check.SE, print = "markdown")
```

<br>

**Netherlands**
```{r}
tadaa_t.test(data = df.check.NL, response = credibility.expert, group = experimental.group, print = "markdown")
```

### Stability

<br>

**Regression**
```{r}
reg.credibility.stability.total.check <- lm(credibility.stability ~  experimental.group,
                    data = df.check,
                    na.action = na.omit)

reg.credibility.stability.SE.check <- lm(credibility.stability ~ experimental.group,
                    data =  df.check.SE,
                    na.action = na.omit)

reg.stability.NL.check <- lm(credibility.stability ~  experimental.group,
                    data =   df.check.NL,
                    na.action = na.omit)

tab_model(reg.credibility.stability.total.check , reg.credibility.stability.SE.check , reg.stability.NL.check , dv.labels = c("Stability - Total", "Stability - SE", "Stability - NL"), title = "Stability - filter: manipulation check", show.ci = FALSE)
```

<br>

**Total**
```{r}
tadaa_aov(credibility.stability ~ experimental.group, data = df.check, print = "markdown")
```

<br>

**Sweden**
```{r}
tadaa_aov(credibility.stability ~ experimental.group, data = df.check.SE, print = "markdown")
```

<br>

**Netherlands**
```{r}
tadaa_t.test(data = df.check.NL, response = credibility.stability, group = experimental.group, print = "markdown")
```

### Non-interference

<br>

**Regression**
```{r}
reg.credibility.noninterference.total.check <- lm(credibility.noninterference ~  experimental.group,
                    data = df.check,
                    na.action = na.omit)

reg.credibility.noninterference.SE.check <- lm(credibility.noninterference ~ experimental.group,
                    data =  df.check.SE,
                    na.action = na.omit)

reg.noninterference.NL.check <- lm(credibility.noninterference ~  experimental.group,
                    data =   df.check.NL,
                    na.action = na.omit)

tab_model(reg.credibility.noninterference.total.check, reg.credibility.noninterference.SE.check, reg.noninterference.NL.check, dv.labels = c("Non-interference - Total", "Non-interference - SE", "Non-interference - NL"), title = "Non-interference - filter: manipulation check", show.ci = FALSE)
```

<br>

**Total**
```{r}
tadaa_aov(credibility.noninterference ~ experimental.group, data = df.check, print = "markdown")
```

<br>

**Sweden**
```{r}
tadaa_aov(credibility.noninterference ~ experimental.group, data = df.check.SE, print = "markdown")
```

<br>

**Netherlands**
```{r}
tadaa_t.test(data = df.check.NL, response = credibility.noninterference, group = experimental.group, print = "markdown")
```

## Only those who spent more time on the introduction page of the case than the median participant

### Histograms
```{r}
ggarrange(df.intro  %>% ggplot(aes(x= credibility.expert, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Total: expertise") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
df.intro.NL %>% ggplot(aes(x= credibility.expert, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Netherlands: expertise") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
df.intro.SE %>% ggplot(aes(x= credibility.expert, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Sweden: expertise") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
df.intro %>% ggplot(aes(x= credibility.stability, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Total: stability") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
 df.intro.NL %>% ggplot(aes(x= credibility.stability, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Netherlands: stability") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
  df.intro.SE %>% ggplot(aes(x= credibility.stability, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Sweden: stability") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
 df.intro %>% ggplot(aes(x= credibility.noninterference, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Total: non-interference") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
df.intro.NL %>% ggplot(aes(x= credibility.noninterference, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Netherlands: non-interference") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
 
df.intro.SE %>% ggplot(aes(x= credibility.noninterference, color = experimental.group)) +
 geom_density(alpha= .1, linetype= "dashed") + theme(axis.title = element_blank()) + labs(y = "", title = "Sweden: non-interference") +  scale_x_continuous(name="", breaks = 1:7) + scale_fill_manual(name = "Condition") +  scale_fill_viridis_d(name = "Condition") + 
  theme_tufte(),
  ncol = 3, nrow = 3, common.legend = TRUE)
```

### Expertise

<br>

**Regression**
```{r}
reg.credibility.expertise.total.intro <- lm(credibility.expert ~  experimental.group,
                    data = df.intro,
                    na.action = na.omit)

reg.credibility.expertise.SE.intro <- lm(credibility.expert ~ experimental.group,
                    data =  df.intro.SE,
                    na.action = na.omit)

reg.credibility.NL.intro <- lm(credibility.expert ~  experimental.group,
                    data =   df.intro.NL,
                    na.action = na.omit)

tab_model(reg.credibility.expertise.total.intro , reg.credibility.expertise.SE.intro, reg.credibility.NL.intro, dv.labels = c("Expertise - Total", "Expertise - SE", "Expertise - NL"), title = "Expertise - filter: introduction of case", show.ci = FALSE)
```

<br>

**Total**
```{r}
tadaa_aov(credibility.expert ~ experimental.group, data = df.intro, print = "markdown")
```

<br>

**Sweden**
```{r}
tadaa_aov(credibility.expert ~ experimental.group, data = df.intro.SE, print = "markdown")
```

<br>

**Netherlands**
```{r}
tadaa_t.test(data = df.intro.NL, response = credibility.expert, group = experimental.group, print = "markdown")
```

### Stability

<br>

**Regression**
```{r}
reg.credibility.stability.total.intro <- lm(credibility.stability ~  experimental.group,
                    data = df.intro,
                    na.action = na.omit)

reg.credibility.stability.SE.intro <- lm(credibility.stability ~ experimental.group,
                    data = df.intro.SE,
                    na.action = na.omit)

reg.stability.NL.intro <- lm(credibility.stability ~  experimental.group,
                    data =   df.intro.NL,
                    na.action = na.omit)

tab_model(reg.credibility.stability.total.intro, reg.credibility.stability.SE.intro, reg.stability.NL.intro , dv.labels = c("Stability - Total", "Stability - SE", "Stability - NL"), title = "Stability -  filter: introduction of case", show.ci = FALSE)
```

<br>

**Total**
```{r}
tadaa_aov(credibility.stability ~ experimental.group, data = df.intro, print = "markdown")
```

<br>

**Sweden**
```{r}
tadaa_aov(credibility.stability ~ experimental.group, data = df.intro.SE, print = "markdown")
```

<br>

**Netherlands**
```{r}
tadaa_t.test(data = df.intro.NL, response = credibility.stability, group = experimental.group, print = "markdown")
```

### Non-interference

<br>

**Regression**
```{r}
reg.credibility.noninterference.total.intro <- lm(credibility.noninterference ~  experimental.group,
                    data = df.intro,
                    na.action = na.omit)

reg.credibility.noninterference.SE.intro <- lm(credibility.noninterference ~ experimental.group,
                    data =  df.intro.SE,
                    na.action = na.omit)

reg.noninterference.NL.intro <- lm(credibility.noninterference ~  experimental.group,
                    data = df.intro.NL,
                    na.action = na.omit)

tab_model(reg.credibility.noninterference.total.intro, reg.credibility.noninterference.SE.intro, reg.noninterference.NL.intro, dv.labels = c("Non-interference - Total", "Non-interference - SE", "Non-interference - NL"), title = "Non-interference - filter: introduction of case", show.ci = FALSE)
```

<br>

**Total**
```{r}
tadaa_aov(credibility.noninterference ~ experimental.group, data = df.intro, print = "markdown")
```

<br>

**Sweden**
```{r}
tadaa_aov(credibility.noninterference ~ experimental.group, data = df.intro.SE, print = "markdown")
```

<br>

**Netherlands**
```{r}
tadaa_t.test(data = df.intro.NL, response = credibility.noninterference, group = experimental.group, print = "markdown")
```


## Explaining credibility
```{r}
library(rockchalk)
model.credibility.index <- lm(credibility.index  ~ perceived.independence.reversed + trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA + credibility.post + familiarity.EMA + familiarity.advice +  political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + poly(age, 2) + healthcare + income + education.recoded + perceived.independence.reversed:benefits.vaccines + benefits.vaccines:experimental.group,
                    data = df.def.error,
                    na.action = na.omit) %>% meanCenter()
  
  model.credibility.stability <- lm(credibility.stability  ~ perceived.independence.reversed + trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA + credibility.post + familiarity.EMA + familiarity.advice +  political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + poly(age, 2) + healthcare + income + education.recoded + perceived.independence.reversed:benefits.vaccines + benefits.vaccines:experimental.group,
                    data = df.def.error,
                    na.action = na.omit) %>% meanCenter()

model.credibility.expertise <- lm(credibility.expert ~ perceived.independence.reversed + trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA + credibility.post + familiarity.EMA + familiarity.advice +  political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + poly(age, 2) + healthcare + income + education.recoded + perceived.independence.reversed:benefits.vaccines + benefits.vaccines:experimental.group,
                    data = df.def.error,
                    na.action = na.omit) %>% meanCenter()

model.credibility.noninterference <- lm(credibility.noninterference ~ perceived.independence.reversed + trust.politicians + trust.scientist + trust.EC + trust.health.authorities + interpersonal.trust + benefits.vaccines + credibility.EMA + credibility.post + familiarity.EMA + familiarity.advice +  political.ideology + consequences.health + consequences.economic + EU.integration + private.providers + knowledge +  experimental.group + female + poly(age, 2) + healthcare + income + education.recoded + perceived.independence.reversed:benefits.vaccines +  benefits.vaccines:experimental.group,
                    data = df.def.error,
                    na.action = na.omit) %>% meanCenter()

tab_model(model.credibility.index, model.credibility.stability, model.credibility.expertise, model.credibility.noninterference, dv.labels = c("Credibility index", "Stability", "Expertise", "Non-interference"), title = "Explaining credibility - index and dimensions", show.ci = FALSE)
```

# Pre-post

## Correlation matrix
```{r}
df.def.error %>% 
  select(credibility.EMA,
         credibility.post,
         credibility.expert,
         credibility.noninterference,
         credibility.stability,
         credibility.index,
         perceived.independence.reversed,
         intent.vaccine,
         ) %>% 
  tab_corr(triangle="lower",
           remove.spaces=T,
           p.numeric = T,
           fade.ns = T,
           digits = 2,
           na.deletion="pairwise",
           title = "Correlation matrix")
```

<br >

## Plot
```{r}
df.def.error  %>% 
  select(experimental.group,
         credibility.EMA,
         credibility.post) %>%  drop_na() %>% 
  gather("key","value",-experimental.group) %>% 
  mutate(key = Recode(key,"'credibility.EMA'='0.Pre';'credibility.post'='1.Post'")) %>%

ggplot(aes(x=key,y=value,color=experimental.group))+
      stat_summary(fun.data = mean_cl_normal, geom = "errorbar", alpha=0.5,width=0.1,size=1,position=position_dodge(0.5)) + 
  stat_summary(fun = mean, geom = "point", alpha=0.5,size=2,position=position_dodge(0.5))+
  stat_summary(fun = mean, geom = "line", alpha=0.5,size=1,position=position_dodge(0.5), aes(group = experimental.group))+
  theme_tufte()
```

<br >

## Regression
```{r}
t1 <- df.def.error %>% mutate(id = row_number()) %>% 
  select(experimental.group,
         id,
         credibility.EMA,
         credibility.post) %>%
  drop_na() %>%
  gather("key","value",-experimental.group,-id) %>% 
  mutate(post = key %>% Recode("'credibility.EMA'= 0;'credibility.post'=1"),
         EMA.credibility = value) 


tmod1 <- lmer(EMA.credibility ~ post + +(1|id),
                       data = t1)

tmod2 <- tmod1 %>% update(.~.+experimental.group) 


tmod3 <- tmod2 %>% update(.~. + post*experimental.group)

tab_model(tmod2,tmod3,
          show.ci = F,
          show.se = T,
          collapse.se = T,
          emph.p = F)
```


# Time

<br>

```{r include=FALSE}
table.duration <- df.def.error %>%
  dplyr::summarize(mean = mean(duration),
            sd = sd(duration),
            min = min(duration),
            q1 = quantile(duration, probs = 0.25),
            median = median(duration),
            q3 = quantile(duration, probs = 0.75),
            max = max(duration)) %>% round(digits = 2)

table.intro.submit <- df.def.error %>% 
   dplyr::summarize(mean = mean(intro.submit),
            sd = sd(intro.submit),
            min = min(intro.submit),
            q1 = quantile(intro.submit, probs = 0.25),
            median = median(intro.submit),
            q3 = quantile(intro.submit, probs = 0.75),
            max = max(intro.submit)) %>% round(digits = 2)

table.manipulation.submit <- df.def.error %>%  
   dplyr::summarize(mean = mean(manipulation.submit, na.rm = TRUE),
            sd = sd(manipulation.submit, na.rm = TRUE),
            min = min(manipulation.submit, na.rm = TRUE),
            q1 = quantile(manipulation.submit, probs = 0.25, na.rm = TRUE),
            median = median(manipulation.submit, na.rm = TRUE),
            q3 = quantile(manipulation.submit, probs = 0.75, na.rm = TRUE),
            max = max(manipulation.submit, na.rm = TRUE)) %>% round(digits = 2)

table.decision.submit <- df.def.error %>% 
   dplyr::summarize(mean = mean(decision.submit),
            sd = sd(decision.submit),
            min = min(decision.submit),
            q1 = quantile(decision.submit, probs = 0.25),
            median = median(decision.submit),
            q3 = quantile(decision.submit, probs = 0.75),
            max = max(decision.submit)) %>% round(digits = 2)
```

<br>

## Survey duration

<br>

### Histogram
```{r}
df.def.error %>% filter(duration < 30) %>% 
plot_frq((duration),
        geom.colors = ggplot2::alpha("red",0.8),
        type = "hist",
        geom.size = 0.25) +
  theme(axis.text = element_text(face = "bold",  size= 9)) + labs(title = "Total survey duration") +  scale_x_continuous(name="Time in minutes", breaks = seq(0,30, 2)) + scale_y_continuous(expand = expansion(c(0, 0.25))) + annotate(geom = "table", x = Inf, y = Inf, label = list(table.duration))
```

<br>


## Do participants read the information about the case?

<br>

### Page submission - introduction of case
```{r}
df.def.error %>% filter(intro.submit < 100) %>%  
plot_frq((intro.submit),
        geom.colors = ggplot2::alpha("dodgerblue2",0.8),
        type = "hist",
        geom.size = 1) + 
  theme(axis.text = element_text(face = "bold",  size= 9)) +
  scale_x_continuous(name="Time in seconds",breaks = seq(0,100,5)) + scale_y_continuous(expand = expansion(c(0, 0.1))) + annotate(geom = "table", x = Inf, y = Inf, label = list(table.intro.submit))
```

<br>


### Page submission - manipulation
```{r}
df.def.error %>% filter(manipulation.submit > 0 & manipulation.submit < 60) %>%  
plot_frq((manipulation.submit),
        geom.colors = ggplot2::alpha("dodgerblue2",0.8),
        type = "hist",
        geom.size = 1) + 
  theme(axis.text = element_text(face = "bold",  size= 9)) +
  scale_x_continuous(name="Time in seconds",breaks = seq(0,100,5)) + scale_y_continuous(expand = expansion(c(0, 0.1))) + annotate(geom = "table", x = Inf, y = Inf, label = list(table.intro.submit))
```

<br>

### Page submission - EMA's decision
```{r}
df.def.error %>% filter(decision.submit < 100) %>% 
plot_frq((decision.submit),
        geom.colors = ggplot2::alpha("dodgerblue2",0.8),
        type = "hist",
        geom.size = 1) + 
  theme(axis.text = element_text(face = "bold",  size= 9)) +
  scale_x_continuous(name= "Time in seconds", breaks = seq(0,100,5)) + scale_y_continuous(expand = expansion(c(0, 0.1))) + annotate(geom = "table", x = Inf, y = Inf, label = list(table.decision.submit))
```

<br>

## Time and ...

<br>

### ...experimental groups
```{r}
p5 <- df.def.error %>% filter(duration < 30) %>% ggplot(aes(x= duration, color = experimental.group, fill = experimental.group)) + geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 2) +
 geom_density(alpha= .1, linetype= "dashed") + labs(title = "Total survey duration", x = "minutes") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

p6  <- df.def.error %>% filter(intro.submit < 60) %>% ggplot(aes(x= intro.submit, color = experimental.group, fill = experimental.group)) + geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 5) +
 geom_density(alpha= .1, linetype= "dashed") + labs(title = "Page submission - introduction", x = "seconds") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))


p8 <- df.def.error %>% filter(decision.submit < 60) %>% ggplot(aes(x=decision.submit, color = experimental.group, fill = experimental.group)) +
 geom_histogram(aes(y=..density..), alpha=0.5, position="identity", binwidth = 5) +
 geom_density(alpha= .1, linetype= "dashed") + labs(title = "Page submission - EMA's decision", x = "seconds") + theme(axis.title.y = element_blank(), title = element_text(size = 7, face = "bold"),  axis.text = element_text(size = 9))

ggarrange(p5, p6, p8, nrow = 2, ncol = 2, labels="AUTO", legend = "bottom", common.legend = TRUE)
```


