---
title: "COVID paper - tables"
author: "Saar Alon-Barkat"
date: "2021"
output:
  html_document:
    code_folding: hide
    fig_captions: yes
    highlight: haddock
    number_sections: yes
    theme: flatly
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
      toc_depth: 3
---

Last update: `r Sys.time()`

```{r set-global-options, echo = FALSE}
knitr::opts_chunk$set(eval = TRUE, 
                      echo = TRUE, 
                      message=FALSE,
                      warning = FALSE,
                      cache = FALSE,
                      include = TRUE,
                      collapse = FALSE,
                      dependson = NULL,
                      engine = "R", #  Chunks will always have R code, unless noted
                      error = TRUE,
                      fig.path="Figures/",  #  Set the figure options
                      fig.align = "left",
                      fig.width = 6,
                      fig.height = 4)
```

```{r silent-packages, echo = FALSE, eval = TRUE, message=FALSE, include = FALSE}
library(sjPlot)
library(tidyverse)
library(car)
library(ggthemes)
library(kableExtra)
library(ggpubr)
library(scales)
library(ggpmisc)
library(tadaatoolbox)
library(stargazer)
library(dotwhisker)
library(broom)
```

<br>

```{r}
source("G:/My Drive/University/R/covid vaccine/paper/DATA_MANIPULATION_POOLED-paper.R")

raw.total <- raw.total %>% 
  mutate(country.lab = country %>% Recode("'NL'='1. Netherlands';
                                          'SE'='2. Sweden';
                                          'IE'='3. Ireland';
                                          'FR'='4. France'"))
pooled <- pooled %>% 
  mutate(country.lab = country %>% Recode("'NL'='1. Netherlands';
                                          'SE'='2. Sweden';
                                          'IE'='3. Ireland';
                                          'FR'='4. France'")) %>% 
  mutate(noninterference.recoded = (noninterference-1)/(7-1),
         expertise.recoded = (expertise-1)/(7-1),
         stability.recoded = (stability-1)/(7-1),
         perceived.independence.reversed.recoded = (perceived.independence.reversed-1)/(7-1))

t1 <- pooled %>% 
  mutate(country = "Total",
    country.lab = "Total")

pooled.1 <- pooled %>% rbind(t1)

t2 <- pooled %>% 
  filter(manipulation.submit>=30) %>%   
  mutate(country = "Total (filtered)",
    country.lab = "Total (filtered)")

pooled.2 <- pooled.1 %>% rbind(t2)

```

<br>

# Descriptive

<br>

## Table of Sample

<br>


```{r}
t1 <- raw.total %>% 
  group_by(country.lab) %>% 
  summarise(
    raw.n=n()
)

t2 <- pooled %>% 
  group_by(country.lab) %>% 
  summarise(
    analytical.n=n(),
    mean.female = mean(female, na.rm=T) %>% round(2),
    mean.age = mean(age, na.rm=T) %>% round(2),
sd.age = sd(age, na.rm=T) %>% round(2)
)

t3 <- raw.total %>% 
  #group_by(country.lab) %>% 
  summarise(
    raw.n=n()
) %>% 
  mutate(country.lab = "5. Total") %>% 
  select(country.lab,raw.n)

t4 <- pooled %>% 
  #group_by(country.lab) %>% 
  summarise(
    analytical.n=n(),
    mean.female = mean(female, na.rm=T) %>% round(2),
    mean.age = mean(age, na.rm=T) %>% round(2),
sd.age = sd(age, na.rm=T) %>% round(2)
) %>% 
  mutate(country.lab = "5. Total")%>% 
  select(country.lab,analytical.n,mean.female,mean.age,sd.age)



t5 <- t1 %>% left_join(t2) %>% 
  rbind(
t3 %>% left_join(t4)
) %>% 
  mutate(
    Age = str_c(mean.age, " (", sd.age, ")"),
    fieldwork = c("19.1.2021 – 25.1.2021",	"25.1.2021 – 31.1.2021",	"28.1.2021 – 20.2.2021",	"10.2.2021 – 17.2.2021",	"19.2.2021 – 20.2.2021")) %>% 
select(country.lab,fieldwork,raw.n,analytical.n,mean.female,Age) %>% t() 

row.names(t5) = c("","Fieldwork","Raw sample","Analytical sample","% Female","Age")


t5 %>% 
  kable()%>%
  kable_styling(bootstrap_options = c("condensed"),
                full_width = F,
                position = "left",
                font_size = 12)

```

<br>



<br>

## Perceived independence of EMA

```{r,fig.width=8,fig.height=4}
p1 <- pooled %>%
  ggplot(aes(x = perceived.independence.reversed)) +
  geom_bar(width = 0.9) + 
  scale_y_continuous(name="") +
  scale_x_continuous(name="", breaks = 1:7) + 
  facet_grid(~country.lab, margins = T) + theme_tufte() + theme(strip.text = element_text(hjust = 0, face = "bold"),
    legend.position="bottom",
    aspect.ratio = 2.5)

p2 <- pooled.1  %>% 
  ggplot(aes(x = country, y = perceived.independence.reversed)) +
      stat_summary(fun.data = mean_cl_normal, geom = "errorbar", alpha = 0.5, width = 0.1, size = 1, position = position_dodge(0.5)) + 
  labs(x = "", y = "") +
    stat_summary(fun = mean, geom = "point", alpha = 0.5, size = 2 , position = position_dodge(0.5)) +  #facet_grid(.~country, margins = TRUE) +  
  theme_tufte() + 
  theme(axis.ticks = element_blank())+
  coord_flip()

ggarrange(p1,p2,widths = c(3,1))


```

<br>

## Distribution of credibility items
```{r}
t1 <- pooled.1  %>% 
  select(country.lab,
         country,
    noninterference.recoded,
    expertise.recoded,
         stability.recoded,
    perceived.independence.reversed.recoded) %>% 
  gather("key", "value", -country.lab,-country) %>%
    mutate(
    key = Recode(
      key,
      "'stability.recoded'='3. Stability';'expertise.recoded'='2. Expert-based';'noninterference.recoded'='1. Non-interference.recoded'"
    )
  ) 

p1 <- t1 %>% 
  ggplot(aes(
    x = key,
    y = value,color = key)) +
  geom_boxplot(width = 0.3) +
  #scale_y_continuous(limits = c(1, 7), breaks = 1:7) +
  scale_x_discrete(
    name = "",
    labels = c("Non-interference",
               "Expert-based",
               "Stability",
               "Perceived independence")
  ) +
  ylab("") +
  theme_tufte() +
  labs(title = "",
       subtitle = "") +
  theme(legend.position = "none")

p2 <- t1  %>% 
  ggplot(aes(x = country, y = value,color = key)) +
      stat_summary(fun.data = mean_cl_normal, geom = "errorbar", alpha = 0.5, width = 0.1, size = 1) + 
  labs(x = "", y = "") +
    stat_summary(fun = mean, geom = "point", alpha = 0.5, size = 2 , position = position_dodge(0.5)) + 
  facet_grid(.~key,scales = "free",space="free") +  
  theme_tufte() + 
  theme(axis.ticks = element_blank(),
        legend.position = "none",
        strip.text.x = element_blank())+
  coord_flip()

ggarrange(p1,p2,nrow =  2,
          heights = c(2,1))
```

<br>

```{r}
p1 <- pooled  %>%
  ggplot(aes(intent.vaccine, group = country.lab)) + 
          geom_bar(aes(y = ..prop..), stat="count") + 
          scale_y_continuous(labels=scales::percent) +
          labs(title = "Ordinal", 
               subtitle = "(1–Very unlikely; 2–Unlikely; 3–Likely; 4–Very Likely)",
               y = "", x = "") +
#  scale_x_continuous(breaks =labels = c("1.Very unlikely", "2.Unlikely","3.Likely", "4.Very Likely"))+
          facet_grid(~country.lab, margins = TRUE) + theme_tufte()

p2 <- pooled.1  %>% 
  ggplot(aes(x = country.lab, y = intent.vaccine.recoded)) +
      stat_summary(fun.data = mean_cl_normal, geom = "errorbar", alpha = 0.5, width = 0.1, size = 1) + 
  labs(title = "Binary",
       subtitle = "(0–Unlikely; 1–Likely)", x = "", y = "") +
  scale_x_discrete(labels = rep("",5)) +
  scale_y_continuous(labels=scales::percent) +
    stat_summary(fun = mean, geom = "point", alpha = 0.5, size = 2 , position = position_dodge(0.5)) + 
  theme_tufte() + 
  theme(axis.ticks = element_blank(),
        legend.position = "none",
        strip.text.x = element_blank())

ggarrange(p1,p2,nrow =  2,
          heights = c(3,2))
```


<br>

# Observational


<br>


## Coefficient plot: observational

```{r}
models.noninterference <- 
pooled.1 %>% 
  group_by(country.lab) %>% 
  do(fit = lm(scale(noninterference.recoded)  ~ 
          scale(perceived.independence.reversed.recoded)+
                            
         female +
         scale(age) +
         
         trust.EU.institutions +
         trust.scientist +
         trust.politicians +
         political.ideology +
         EU.integration +
         interpersonal.trust +
         familiarity.EMA +
         familiarity.advice +
         trust.health.authorities +
         consequences.health +
         consequences.economic +
         benefits.vaccines,
         data = .,
         na.action = na.omit))

models.expertise <- 
pooled.1 %>% 
  group_by(country.lab) %>% 
  do(fit = lm(scale(expertise.recoded)  ~ 
          scale(perceived.independence.reversed.recoded)+
                            
         female +
         scale(age) +
         
         trust.EU.institutions +
         trust.scientist +
         trust.politicians +
         political.ideology +
         EU.integration +
         interpersonal.trust +
         familiarity.EMA +
         familiarity.advice +
         trust.health.authorities +
         consequences.health +
         consequences.economic +
         benefits.vaccines,
         data = .,
         na.action = na.omit))

models.stability <- 
pooled.1 %>% 
  group_by(country.lab) %>% 
  do(fit = lm(scale(stability.recoded)  ~ 
          scale(perceived.independence.reversed.recoded)+
                            
         female +
         scale(age) +
         
         trust.EU.institutions +
         trust.scientist +
         trust.politicians +
         political.ideology +
         EU.integration +
         interpersonal.trust +
         familiarity.EMA +
         familiarity.advice +
         trust.health.authorities +
         consequences.health +
         consequences.economic +
         benefits.vaccines,
         data = .,
         na.action = na.omit))

models.intent.vaccine <- 
pooled.1 %>% 
  group_by(country.lab) %>% 
  do(fit = glm(intent.vaccine.recoded  ~ 
          scale(perceived.independence.reversed.recoded)+
                            
         female +
         scale(age) +
         
         trust.EU.institutions +
         trust.scientist +
         trust.politicians +
         political.ideology +
         EU.integration +
         interpersonal.trust +
         familiarity.EMA +
         familiarity.advice +
         trust.health.authorities +
         consequences.health +
         consequences.economic +
         benefits.vaccines,
         data = .,
         family = "binomial",
         na.action = na.omit))


p1 <- rbind(models.noninterference$fit[[1]] %>% tidy() %>% mutate(model="NL"), 
models.noninterference$fit[[2]] %>% tidy() %>% mutate(model="SE"),
models.noninterference$fit[[3]] %>% tidy() %>% mutate(model="IE"),
models.noninterference$fit[[4]] %>% tidy() %>% mutate(model="FR"),
models.noninterference$fit[[5]] %>% tidy() %>% mutate(model="All")
) %>% filter(term=="scale(perceived.independence.reversed.recoded)")%>%
  dwplot(dodge_size=0.2,
                dot_args = list(size = 3),
  whisker_args = list(size = 0.7),
  vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2)) %>% 
      relabel_predictors(c(`scale(perceived.independence.reversed.recoded)` = ""))+
  theme_tufte()+
  scale_color_viridis_d(name = "Country", guide = guide_legend(reverse=TRUE))+
  ggtitle("Non-interference")

p2 <- rbind(models.expertise$fit[[1]] %>% tidy() %>% mutate(model="NL"), 
models.expertise$fit[[2]] %>% tidy() %>% mutate(model="SE"),
models.expertise$fit[[3]] %>% tidy() %>% mutate(model="IE"),
models.expertise$fit[[4]] %>% tidy() %>% mutate(model="FR"),
models.expertise$fit[[5]] %>% tidy() %>% mutate(model="All")
) %>% filter(term=="scale(perceived.independence.reversed.recoded)")%>%
  dwplot(dodge_size=0.2,
                dot_args = list(size = 3),
  whisker_args = list(size = 0.7),
  vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2))%>% 
      relabel_predictors(c(`scale(perceived.independence.reversed.recoded)` = "")) +
  theme_tufte()+
  scale_color_viridis_d(name = "Country", guide = guide_legend(reverse=TRUE))+
  ggtitle("Expert-based")


p3 <- rbind(models.stability$fit[[1]] %>% tidy() %>% mutate(model="NL"), 
models.stability$fit[[2]] %>% tidy() %>% mutate(model="SE"),
models.stability$fit[[3]] %>% tidy() %>% mutate(model="IE"),
models.stability$fit[[4]] %>% tidy() %>% mutate(model="FR"),
models.stability$fit[[5]] %>% tidy() %>% mutate(model="All")
) %>% filter(term=="scale(perceived.independence.reversed.recoded)")%>%
  dwplot(dodge_size=0.2,
                dot_args = list(size = 3),
  whisker_args = list(size = 0.7),
  vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2)) %>% 
      relabel_predictors(c(`scale(perceived.independence.reversed.recoded)` = ""))+
  theme_tufte()+
  scale_color_viridis_d(name = "Country", guide = guide_legend(reverse=TRUE))+
  ggtitle("Stability")





ggarrange(p1,p2,p3,
          ncol = 3,nrow = 1,
          common.legend = T,
          legend = "right")

```


<br>


## Bivariate descriptive correlations: observational

```{r,fig.height=8,fig.width=4}

p1 <- pooled %>% 
  ggplot(aes(x=factor(perceived.independence.reversed.recoded),y=noninterference.recoded))+
      stat_summary(fun.data = mean_cl_normal, geom = "errorbar", color="skyblue",alpha=0.5,width=0.1,size=1,position=position_dodge(0.5)) + 
  stat_summary(fun = mean, geom = "point",color="skyblue", alpha=0.5,size=2,position=position_dodge(0.5))+
  stat_summary(fun = mean, geom = "line", alpha=0.5,size=1,position=position_dodge(0.5), aes(group = 1)) + 
    labs(color ='Experimental group', x = "", y = "") +
  scale_x_discrete(breaks = c(0,0.5,1))+
    facet_grid(~country, margins = TRUE) +
  ggtitle("Non-Interference")+
  theme_tufte()


p2 <- pooled %>% 
  ggplot(aes(x=factor(perceived.independence.reversed.recoded),y=expertise.recoded))+
      stat_summary(fun.data = mean_cl_normal, geom = "errorbar", color="skyblue",alpha=0.5,width=0.1,size=1,position=position_dodge(0.5)) + 
  stat_summary(fun = mean, geom = "point",color="skyblue", alpha=0.5,size=2,position=position_dodge(0.5))+
  stat_summary(fun = mean, geom = "line", alpha=0.5,size=1,position=position_dodge(0.5), aes(group = 1)) + 
    labs(color ='Experimental group', x = "", y = "") +
  scale_x_discrete(breaks = c(0,0.5,1))+
    facet_grid(~country, margins = TRUE) +
  ggtitle("Expert-based")+
  theme_tufte()

p3 <- pooled %>% 
  ggplot(aes(x=factor(perceived.independence.reversed.recoded),y=stability.recoded))+
      stat_summary(fun.data = mean_cl_normal, geom = "errorbar", color="skyblue",alpha=0.5,width=0.1,size=1,position=position_dodge(0.5)) + 
  stat_summary(fun = mean, geom = "point",color="skyblue", alpha=0.5,size=2,position=position_dodge(0.5))+
  stat_summary(fun = mean, geom = "line", alpha=0.5,size=1,position=position_dodge(0.5), aes(group = 1)) + 
    labs(color ='Experimental group', x = "", y = "") +
  scale_x_discrete(breaks = c(0,0.5,1))+
    facet_grid(~country, margins = TRUE) +
  ggtitle("Stability")+
  theme_tufte()


p4<- pooled %>% 
  ggplot(aes(x=factor(perceived.independence.reversed.recoded),y=intent.vaccine.recoded))+
      stat_summary(fun.data = mean_cl_normal, geom = "errorbar", color="skyblue",alpha=0.5,width=0.1,size=1,position=position_dodge(0.5)) + 
  stat_summary(fun = mean, geom = "point",color="skyblue", alpha=0.5,size=2,position=position_dodge(0.5))+
  stat_summary(fun = mean, geom = "line", alpha=0.5,size=1,position=position_dodge(0.5), aes(group = 1)) + 
    labs(color ='Experimental group', x = "", y = "") +
  scale_x_discrete(breaks = c(0,0.5,1))+
    facet_grid(~country, margins = TRUE) +
  ggtitle("Intent to vaccinate")+
  theme_tufte()

ggarrange(p1,p2,p3,p4,
          ncol = 1,nrow = 4)

```


## Coefficients table for intent to vaccinate: observational

```{r}


t1 <- rbind(
  models.intent.vaccine$fit[[1]] %>% tidy() %>% mutate(estimate = exp(estimate))%>% 
  mutate(conf.low = exp(confint(models.intent.vaccine$fit[[1]])) %>% data.frame() %>% .$X2.5.., 
  conf.high = exp(confint(models.intent.vaccine$fit[[1]])) %>% data.frame() %>% .$X97.5..) %>% mutate(model="NL"),
  
models.intent.vaccine$fit[[2]] %>% tidy() %>% mutate(estimate = exp(estimate))%>% 
  mutate(conf.low = exp(confint(models.intent.vaccine$fit[[2]])) %>% data.frame() %>% .$X2.5..,
         conf.high = exp(confint(models.intent.vaccine$fit[[2]])) %>% data.frame() %>% .$X97.5..)%>% mutate(model="SE"),

models.intent.vaccine$fit[[3]] %>% tidy() %>% mutate(estimate = exp(estimate))%>% 
  mutate(conf.low = exp(confint(models.intent.vaccine$fit[[3]])) %>% data.frame() %>% .$X2.5..,
         conf.high = exp(confint(models.intent.vaccine$fit[[3]])) %>% data.frame() %>% .$X97.5..)%>% mutate(model="IE"),

models.intent.vaccine$fit[[4]] %>% tidy() %>% mutate(estimate = exp(estimate))%>% 
  mutate(conf.low = exp(confint(models.intent.vaccine$fit[[4]])) %>% data.frame() %>% .$X2.5..,
         conf.high = exp(confint(models.intent.vaccine$fit[[5]])) %>% data.frame() %>% .$X97.5..)%>% mutate(model="FR"),

models.intent.vaccine$fit[[5]] %>% tidy() %>% mutate(estimate = exp(estimate))%>% 
  mutate(conf.low = exp(confint(models.intent.vaccine$fit[[5]])) %>% data.frame() %>% .$X2.5..,
         conf.high = exp(confint(models.intent.vaccine$fit[[5]])) %>% data.frame() %>% .$X97.5..) %>% mutate(model="All")
) %>% filter(term=="scale(perceived.independence.reversed.recoded)")
  

t1 %>% 
    select(model,estimate,conf.low,conf.high,p.value) %>% 
  mutate(across(2:5, round, 3)) %>% 
    mutate(CI = str_c("[",conf.low, ", ", conf.high, "]")) %>% 
    select(Country=model,OR=estimate,CI,p.value) %>% 
    kable()%>%
  kable_styling(bootstrap_options = c("condensed"),
                full_width = F,
                position = "left",
                font_size = 12)
  


```


<br>

# Experimental

<br>

## Coefficient plot: manipulation check

```{r,fig.width=6}
models.man.check <- 
pooled.2 %>% 
  group_by(country.lab) %>% 
  do(fit = lm(scale(perceived.independence.reversed.recoded)  ~ 
          experimental.group,
         data = .,
         na.action = na.omit))

p1 <- rbind(models.man.check$fit[[1]] %>% tidy() %>% mutate(model="NL"), 
models.man.check$fit[[2]] %>% tidy() %>% mutate(model="SE"),
models.man.check$fit[[3]] %>% tidy() %>% mutate(model="IE"),
models.man.check$fit[[4]] %>% tidy() %>% mutate(model="FR"),
models.man.check$fit[[5]] %>% tidy() %>% mutate(model="All"),
models.man.check$fit[[6]] %>% tidy() %>% mutate(model="All (filtered)")
) %>% filter(term=="experimental.groupindependence")%>%
  dwplot(dodge_size=0.2,
                dot_args = list(size = 3),
  whisker_args = list(size = 0.7),
  vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2)) %>% 
      relabel_predictors(c(experimental.groupindependence = ""))+
  theme_tufte()+
  scale_color_viridis_d(name = "Country", guide = guide_legend(reverse=TRUE))+
  labs(title = "perceived independence",ylab="")


p1
```

<br>

```{r,fig.width=8}


models.noninterference <- 
pooled.2 %>% 
  group_by(country.lab) %>% 
  do(fit = lm(scale(noninterference.recoded)  ~ 
          experimental.group,
         data = .,
         na.action = na.omit))

models.expertise <- 
pooled.2 %>% 
  group_by(country.lab) %>% 
  do(fit = lm(scale(expertise.recoded)  ~ 
          experimental.group,
         data = .,
         na.action = na.omit))

models.stability <- 
pooled.2 %>% 
  group_by(country.lab) %>% 
  do(fit = lm(scale(stability.recoded)  ~ 
          experimental.group,
         data = .,
         na.action = na.omit))

models.intent.vaccine <- 
pooled.2 %>% 
  group_by(country.lab) %>% 
  do(fit = glm(intent.vaccine.recoded  ~ 
          experimental.group,
         data = .,
         family = "binomial",
         na.action = na.omit))


p2 <- rbind(models.noninterference$fit[[1]] %>% tidy() %>% mutate(model="NL"), 
models.noninterference$fit[[2]] %>% tidy() %>% mutate(model="SE"),
models.noninterference$fit[[3]] %>% tidy() %>% mutate(model="IE"),
models.noninterference$fit[[4]] %>% tidy() %>% mutate(model="FR"),
models.noninterference$fit[[5]] %>% tidy() %>% mutate(model="All"),
models.noninterference$fit[[6]] %>% tidy() %>% mutate(model="All (filtered)")
) %>% filter(term=="experimental.groupindependence")%>%
  dwplot(dodge_size=0.2,
                dot_args = list(size = 3),
  whisker_args = list(size = 0.7),
  vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2)) %>% 
      relabel_predictors(c(experimental.groupindependence = ""))+
  theme_tufte()+
  scale_color_viridis_d(name = "Country", guide = guide_legend(reverse=TRUE))+
  labs(title = "Non-interference",ylab="")

p3 <- rbind(models.expertise$fit[[1]] %>% tidy() %>% mutate(model="NL"), 
models.expertise$fit[[2]] %>% tidy() %>% mutate(model="SE"),
models.expertise$fit[[3]] %>% tidy() %>% mutate(model="IE"),
models.expertise$fit[[4]] %>% tidy() %>% mutate(model="FR"),
models.expertise$fit[[5]] %>% tidy() %>% mutate(model="All"),
models.expertise$fit[[6]] %>% tidy() %>% mutate(model="All (filtered)")
) %>% filter(term=="experimental.groupindependence")%>%
  dwplot(dodge_size=0.2,
                dot_args = list(size = 3),
  whisker_args = list(size = 0.7),
  vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2)) %>% 
      relabel_predictors(c(experimental.groupindependence = ""))+
  theme_tufte()+
  scale_color_viridis_d(name = "Country", guide = guide_legend(reverse=TRUE))+
  labs(title = "Expertise",ylab="")

p4 <- rbind(models.stability$fit[[1]] %>% tidy() %>% mutate(model="NL"), 
models.stability$fit[[2]] %>% tidy() %>% mutate(model="SE"),
models.stability$fit[[3]] %>% tidy() %>% mutate(model="IE"),
models.stability$fit[[4]] %>% tidy() %>% mutate(model="FR"),
models.stability$fit[[5]] %>% tidy() %>% mutate(model="All"),
models.stability$fit[[6]] %>% tidy() %>% mutate(model="All (filtered)")
) %>% filter(term=="experimental.groupindependence")%>%
  dwplot(dodge_size=0.2,
                dot_args = list(size = 3),
  whisker_args = list(size = 0.7),
  vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2)) %>% 
      relabel_predictors(c(experimental.groupindependence = ""))+
  theme_tufte()+
  scale_color_viridis_d(name = "Country", guide = guide_legend(reverse=TRUE))+
  labs(title = "Stability",ylab="")


ggarrange(p2,p3,p4,
          ncol = 3,nrow = 1,
          common.legend = T,
          legend = "right")
```


<br>


## Coefficients table for intent to vaccinate: experimental


```{r}


t1 <- rbind(
  models.intent.vaccine$fit[[1]] %>% tidy() %>% mutate(estimate = exp(estimate))%>% 
  mutate(conf.low = exp(confint(models.intent.vaccine$fit[[1]])) %>% data.frame() %>% .$X2.5.., 
  conf.high = exp(confint(models.intent.vaccine$fit[[1]])) %>% data.frame() %>% .$X97.5..) %>% mutate(model="NL"),
  
models.intent.vaccine$fit[[2]] %>% tidy() %>% mutate(estimate = exp(estimate))%>% 
  mutate(conf.low = exp(confint(models.intent.vaccine$fit[[2]])) %>% data.frame() %>% .$X2.5..,
         conf.high = exp(confint(models.intent.vaccine$fit[[2]])) %>% data.frame() %>% .$X97.5..)%>% mutate(model="SE"),

models.intent.vaccine$fit[[3]] %>% tidy() %>% mutate(estimate = exp(estimate))%>% 
  mutate(conf.low = exp(confint(models.intent.vaccine$fit[[3]])) %>% data.frame() %>% .$X2.5..,
         conf.high = exp(confint(models.intent.vaccine$fit[[3]])) %>% data.frame() %>% .$X97.5..)%>% mutate(model="IE"),

models.intent.vaccine$fit[[4]] %>% tidy() %>% mutate(estimate = exp(estimate))%>% 
  mutate(conf.low = exp(confint(models.intent.vaccine$fit[[4]])) %>% data.frame() %>% .$X2.5..,
         conf.high = exp(confint(models.intent.vaccine$fit[[5]])) %>% data.frame() %>% .$X97.5..)%>% mutate(model="FR"),

models.intent.vaccine$fit[[5]] %>% tidy() %>% mutate(estimate = exp(estimate))%>% 
  mutate(conf.low = exp(confint(models.intent.vaccine$fit[[5]])) %>% data.frame() %>% .$X2.5..,
         conf.high = exp(confint(models.intent.vaccine$fit[[5]])) %>% data.frame() %>% .$X97.5..) %>% mutate(model="All"),

models.intent.vaccine$fit[[6]] %>% tidy() %>% mutate(estimate = exp(estimate))%>% 
  mutate(conf.low = exp(confint(models.intent.vaccine$fit[[6]])) %>% data.frame() %>% .$X2.5..,
         conf.high = exp(confint(models.intent.vaccine$fit[[6]])) %>% data.frame() %>% .$X97.5..) %>% mutate(model="All (filtered)")
) %>% filter(term=="experimental.groupindependence")
  

t1 %>% 
    select(model,estimate,conf.low,conf.high,p.value) %>% 
  mutate(across(2:5, round, 3)) %>% 
    mutate(CI = str_c("[",conf.low, ", ", conf.high, "]")) %>% 
    select(Country=model,OR=estimate,CI,p.value) %>% 
    kable()%>%
  kable_styling(bootstrap_options = c("condensed"),
                full_width = F,
                position = "left",
                font_size = 12)
  


```




<br>

# Regression tables


<br>

## Observational

```{r}
tmod1 <- lm(noninterference  ~ 
          perceived.independence.reversed+
          country,
         data = pooled,
         na.action = na.omit)
         
tmod2 <- tmod1 %>% update(.~.+
                            
         female +
         scale(age) +
         
         trust.EU.institutions +
         trust.scientist +
         trust.politicians +
         political.ideology +
         EU.integration +
         interpersonal.trust +
         familiarity.EMA +
         familiarity.advice +
         trust.health.authorities +
         consequences.health +
         consequences.economic +
         benefits.vaccines,
         data = pooled,
         na.action = na.omit)

tmod3 <- tmod1 %>% update(expertise~.)

tmod4 <- tmod2 %>% update(expertise~.)


tmod5 <- tmod1 %>% update(stability~.)

tmod6 <- tmod2 %>% update(stability~.)

tmod7 <-  glm(intent.vaccine.recoded  ~ 
          perceived.independence.reversed+
          country,
         data = pooled,
         family = "binomial",
         na.action = na.omit)

tmod8 <- tmod7 %>% update(.~.+
                            
         female +
         scale(age) +
         
         trust.EU.institutions +
         trust.scientist +
         trust.politicians +
         political.ideology +
         EU.integration +
         interpersonal.trust +
         familiarity.EMA +
         familiarity.advice +
         trust.health.authorities +
         consequences.health +
         consequences.economic +
         benefits.vaccines)


tab_model(tmod1,tmod2,tmod3,tmod4,tmod5,tmod6,tmod7,tmod8,
          #collapse.ci = T,
          emph.p = F,
          show.se = T,
          show.ci = F,
          collapse.se = T)
```

<br>


## Experimental

<br>

```{r}
tmod1 <- lm(noninterference  ~ 
          experimental.group+
          country,
         data = pooled,
         na.action = na.omit)
         
tmod2 <- tmod1 %>% update(.~.+
                            
         female +
         scale(age) +
         
         trust.EU.institutions +
         trust.scientist +
         trust.politicians +
         political.ideology +
         EU.integration +
         interpersonal.trust +
         familiarity.EMA +
         familiarity.advice +
         trust.health.authorities +
         consequences.health +
         consequences.economic +
         benefits.vaccines,
         data = pooled,
         na.action = na.omit)

tmod1a <- tmod1 %>% update(.~., data = pooled %>% filter(manipulation.submit>=30))
tmod2a <- tmod2 %>% update(.~., data = pooled %>% filter(manipulation.submit>=30))


tmod3 <- tmod1 %>% update(expertise~.)
tmod4 <- tmod2 %>% update(expertise~.)

tmod3a <- tmod3 %>% update(.~., data = pooled %>% filter(manipulation.submit>=30))
tmod4a <- tmod4 %>% update(.~., data = pooled %>% filter(manipulation.submit>=30))


tmod5 <- tmod1 %>% update(stability~.)
tmod6 <- tmod2 %>% update(stability~.)

tmod5a <- tmod5 %>% update(.~., data = pooled %>% filter(manipulation.submit>=30))
tmod6a <- tmod6 %>% update(.~., data = pooled %>% filter(manipulation.submit>=30))

tmod7 <-  glm(intent.vaccine.recoded  ~ 
          experimental.group+
          country,
         data = pooled,
         family = "binomial",
         na.action = na.omit)

tmod8 <- tmod7 %>% update(.~.+
                            
         female +
         scale(age) +
         
         trust.EU.institutions +
         trust.scientist +
         trust.politicians +
         political.ideology +
         EU.integration +
         interpersonal.trust +
         familiarity.EMA +
         familiarity.advice +
         trust.health.authorities +
         consequences.health +
         consequences.economic +
         benefits.vaccines)


tmod7a <- tmod7 %>% update(.~., data = pooled %>% filter(manipulation.submit>=30))
tmod8a <- tmod8 %>% update(.~., data = pooled %>% filter(manipulation.submit>=30))


tmod9 <- tmod1 %>% update(perceived.independence.reversed~.)
tmod10 <- tmod2 %>% update(perceived.independence.reversed~.)

tmod9a <- tmod9 %>% update(.~., data = pooled %>% filter(manipulation.submit>=30))
tmod10a <- tmod10 %>% update(.~., data = pooled %>% filter(manipulation.submit>=30))

```

<br>

```{r}
tab_model(tmod9,tmod10,
          tmod9a,tmod10a,
          #collapse.ci = T,
          emph.p = F,
          show.se = T,
          show.ci = F,
          collapse.se = T)
```

```{r}

tab_model(tmod1,tmod2,
          tmod3,tmod4,
          tmod5,tmod6,
          #collapse.ci = T,
          emph.p = F,
          show.se = T,
          show.ci = F,
          collapse.se = T)
```

<br>

```{r}
tab_model(tmod1a,tmod2a,
          tmod3a,tmod4a,
          tmod5a,tmod6a,
          #collapse.ci = T,
          emph.p = F,
          show.se = T,
          show.ci = F,
          collapse.se = T)
```


<br>

```{r}
tab_model(tmod7,tmod8,tmod7a,tmod8a,
          #collapse.ci = T,
          emph.p = F,
          show.se = T,
          show.ci = F,
          collapse.se = T)
```


